\documentclass[a4paper]{article}
\begin{document}
\hsize=140mm
\leftskip=-20mm
{\noindent \Huge  A Family History}

{\it Robert R. Pavlis}
\vskip 6mm
	This is a volume of family history.  The Bogenhagen section is rewritten from a Bogenhagen family history originally compiled by Kathy Bogenhagen Ostrem.  The Ketelhut section is the work of Arthur Grulke.  I have also added information about the Pavlis family, the Jasch family, and the Sharping family, and added many entries to both the Ketelhut and Bogenhagen history.  I have put all families into a constant format so that people who occur in more than one family will occur at the same outline level.  This makes it very simple to determine how different people are related to one another.

\noindent   The outline levels in order are:

	1. Capital Roman numbers, I, II, III, etc.	
	2. Capital Roman letters, A,B,C, etc.
	3. Arabic numbers, 1,2,3, etc.
	4. Lower case Roman letters, a,b,c,etc.
	5. Double lower case Roman letters, aa, bb, cc, etc.
	6. Triple lower case Roman letters, aaa, bbb, ccc, etc.  
  
\noindent How am I related to whom?

	If two people have the same parents they are brothers or sisters.
	If two people have the same grandparents they are cousins.
	If two people have the same great grandparents they are second cousins.
	If two people have the same great great grandparents they are third cousins.  
	A person's sibling's children are nieces and nephews.
	A person's parent's siblings are aunts and uncles.
	A person's sibling's grandchildren are grandnieces or grandnephews.
	A person's grandparent's siblings are great aunts or great uncles.
	When two people are related so that one has the same grandparent as the other one's great grandparent, these people are cousins once removed.  
	Two people who are related so that one has the same great grandparent as the other one has great great grandparents are second cousins once removed.
	In this manner nth cousins m times removed can be defined!

	This history his designed to be extendable.  I took great pains to make each family totally independent of the others.  Relatives who are not related to all the people in this volume can remove the part of the volume not related to them, and can add more relatives.  It would be best if the same outline were followed as used here to avoid confusion.

\pagebreak

{\Huge \noindent Pavlis Family}
\vskip 5mm

	The early history of the Pavlis family that migrated to what is now southern South Dakota in the latter half of the nineteenth century from Europe is somewhat nebulous.  Although they came to the Dakota Territory from an area of the Austro-Hungarian Empire about 100 km south east of Prague, the name Pavlis is not Slavic at all, it is Greek!   It seems almost certain that an earlier ancestor named $\mathnormal{\Pi\alpha\beta\lambda\iota\sigma}$ fled the oppressive Ottoman empire, probably sometime during the late eighteenth or early nineteen century.  
	The name Pavlis was spelled Pavli\v{s} in Europe.  On arrival in America some members of the family spelled it Pavlis, others Pavlish.  The problem was that the letter \v{s} does not occur in English!    
	The earliest known male ancestor was born about 1830 in Telecin, now the Czech Republic.  Documents examined by Robert Pavlis and Agnes Engel in the late 1980's indicated that his name was Josef.  Oddly Jaroslav Pavlis said that his father had said his name was Anton.  The documents, however,  were quite unequivocal.  Anton must have been Josef's Father, or else he used his middle name.  
	Another group of Pavlis family members migrated to Michigan from the area of Tabor, very near Telecin and Poli\v{c}ka.  They almost certainly are relatives, although the exact connexion is not known.  It is likely that they are decendents of a brother or cousin of Josef. 

I. Josef Pavli\v{s} was born in Telecin about 1830.  He died in Europe.  He married Anna Ku\v{c}era who was born in 1832 in Telecin.  She migrated to the United States with her youngest children in about 1890.  She lived with her son James and his wife on homested plots south west of the present site of Geddes, S.D.  from her arrival until about 1900 when they moved to another farm in White Swan township that was later occupied by Louie and Charlie Pavlis.  She died on 18 March 1917.  She is buried in the small cemetary west of Geddes Lake.  A local farmer, the late Harold Robinson, removed tomb stones from the site to prop up his porch.  The grave was unmarked until 2004 when a group of relatives placed a tombstone on the site.   
\vskip 6mm
A. Josef Pavli\v{s} was born in 1856.  He died on 8 December 1920.  He married Emilie Plihal. (Lorraine Augspurger is fairly certain this was 1929, other information said 1927.)

1.Emilie Pavlis was born on 10 September 1884.  She died on 10 Jan 1979.  She was first married to James Kandl, and later married August Hegar.

a. Rose Kandl was born in 1905.  She died in 1974.  

b. Mabel Hegar was born in 1920.  She died in 1990.  Two siblings died in infancy.

2. Josephine Pavlis was born on 1 May 1886.  She died in September 1959. She married John Stekly II.

a. John Stekly III was born on 28 August 1913.  He married Helen Billars.

aa. John Stekly IV was born 31 May 1947.  He married Karen J. Schwartz..  (optometrist)

aaa. John Stekly V was born 4 Feb 1977.

3. Joseph Pavlis was born 16 September 1888.  He died 6 September 1976.  He married Elsie Fijala.

a. Lawrence Pavlis was born on 06 July 1921.  He died on 18 July 1994. He was married to Clarabelle Clark.

aa. Larry Pavlis.

bb. Linda Pavlis was born in 1948.

cc. Dale Pavlis was born in 1953.

dd. LeAnn Pavlis was born about 1955.

b. William A. Pavlis was born on 28 Dec 1922.  He married Patricia Wood.

c. Lorraine Pavlis was born on 10 March 1924.  She married Kenneth Augspurger.

aa. Ken Augspurger was born on 1 March 1951.  He was married to Mariann Holbach. (He is an optholmologist in Sioux Falls.)

4. Marie Pavlis was born on 9 November 1892.  She died on 26 Nov 1981.  She married James Kadlec.

5. Jaroslav Pavlis was born 27 July 1894.  He died on 12 May 1981.  He married Rose Belle Fijala.  

a.  Harold Pavlis was born on 13 December 1922.  He married Iona Nelson.  

aa. Lyle Pavlis was born 29 August 1944.  He married Judi Aune.

bb. Cheryl Pavlis was born 18 Feb 1947.  She married Robert Jaeger.

cc. Jean Pavlis was born on 18 Jan 1952.  She was married to Dale Sybesma.

dd. Vicky Pavlis was born 14 July 1962.

b. Beatrice Pavlis was born in April 1924.  She married Victor Mushitz.

c. Jaroslav Duane Pavlis was born in 1930.  He was always known as Sonny.

6. Rusena Pavlis was born 6 July 1897.  She died in 1989.  She was married to Louis Teply.

a. Roy Teply was born on 6 Feb 1923.  He married Elaine Owens.

b. Leo Teply was born on 24 Sept 1924.  

c. Ruby Teply was born on 26 Oct 1929.

d. Wilma Teply was born on 1 March 1933.  She married Charles Slaba.

7. Amalka Pavlis was born on 13 May 1900.  She died on 10 Dec 1989.  She was always known as Millie.

8. Mildred Pavlis was born on 29 March 1906.  She died on 18 June 1906.

9. Emil Pavlis was born 8 Jan 1908.  He departed from this life on 14 Jan 1981. He was married to Gerda Baumiller.

B. Antonin Pavli\v{s} was born in 1857.  He died on Europe on 7 Jan 1938. 

C. Adolph Pavli\v{s} was born in 28 Dec 1862.  He died in 1943  He married Lydia Dittmar. He came to America in 1886.  

1. Edwin Pavlis was born about 1890.  He died on 6 March 1973 in an auto accident. 

2. John Pavlis was born 23 July 1883.  He died 20 Sept 1978. He married Anna Rezek.

D.  James Pavli\v{s} was born on 2 October 1867 in Polecka.  He died in September 1947.  He married Anna  Dufek.  She, oddly, never told any of her children anything about her family.  It is known, however, that she had a brother named Frank who lived much of his life in Oklahoma, and at least two  sisters, one was married to John Travnicek of Tyndall South Dakota, and the other to a Hermann.  Rumour has it that her parents were buried in Centerville, South Dakota.  Anna Dufek was born on 7 May 1871 and died in 1938. The birth date on her tombstone in Lake Andes, South Dakota is incorrect. She was born in Moravia.  William thought her Father's name was Frank.  

1. Charles Pavlis was born on 13 May 1899.  He died in March of 1960.  

2. Louie Pavlis was born 13 May 1902.  He died on 6 October 1989.

3. Albia Pavlis was born on 14 February 1904.  She was married to Leroy F.Booher. She departed from this life in October 1997.

a. Betty Booher was  born on 7 May 1928.  She died on 16 May 1980. (Diabetes induced  Heart attack)  She married Vern Milton Creasey.

aa. Kenneth Richard Creasey was born 19 Feb 1949.  He was married to Mary Ann Guthrie.

aaa. Leign Ann Creasey was born 28 Nov 1980.

bb. Colleen Kay Creasey was born 16 Nov 1954.  She was married to Lawrence John Jaeger.

aaa. Kevin Michael Jaeger was born 18 Sept 1979.

bbb. Michelle Lenae Jaeger was born 4 June 1982.

ccc. Brian Dean Jaeger was born 9 March 1984.
					
cc. Robert Dean Creasey was born on 30 Oct 1962.  He was married to Lisa Lynn VanZee.

b. JoAnn Booher was born on 11 Jan 1931.  She married George Joseph Sully in 1950.  She divorced and much later married Arthur Delperdang.

aa. George Roy Sully was born on 2 October 1950.  He was married to Kathleen Ann Kwikkel.

aaa. Kelly Jo Sully was born 11 May 1973.

bbb. George Dean Sully was born 4 June 1974.

ccc. Heidi Jo Sully was born 11 Feb 1983.  

ddd. Randi Jo Sully was born 22 July 1984.

eee. Katy Jo Sully was born 18 July 1986.

4. Tom Pavlis was born in 10 July 1905.  He died on 25 March1975.  He was married to	Clara Slaba.   

5. Mary Pavlis was born 5 April 1907.  She died in 1935.  She married Nick VanHeest. 
 
a.  Melvin VanHeest, (Rumour has it that his father was one of the Hrdlicka family.)  

b. Thelma VanHeest was born in 1928. (Rumour has it that her father was one of the Soulek brothers of Lake Andes.)

c. Anne VanHeest was born in about 1931.  She died in 1945 under very suspicious circumstances; family  always thought feloneous, with Nick at fault, as he was apparently in Mary's death from illegal abortion.   

6. Josephine Pavlis was born on 10 July 1909. She departed from this life on 2 January 1997.  She married Stanley Ellis.  They lived in Ohio for many  years where he worked with the rubber industry. 

a. Allen James Ellis was born on 2 March 1947.  He married Marilyn Carol Habeeb.

aa. Christopher Watson Ellis was born 16 Feb 1971.

bb. Scott Allen Ellis was born 27 Sept 1972.

7. William Pavlis was born on 15 August 1912.  He married Stella Clara Bertha Bogenhagen on 27 December 1938.  He died on 4 January 1984.

a. Robert Roy Pavlis was born on 10 April 1941. 

b. Roger Dean Pavlis was born 14 June 1946.  He was married to Karen Knutson, born 20 June 1946, on 9 June 1967.

aa.  Chad Loren Pavlis was born on 12 August 1969.  He was married to Amy Marie Peterson on 9 June 1991.

bb. Jeremy Mark Pavlis was born on 25 Sept 1972.  He was married on 10 June 1995 to Anne Elizabeth Geise.

c. Joyce Ann Pavlis was born on 18 January 1949.  She married on 13 July 1975 to Everett Tollerud, born 9 Feb 1949.  

aa. Heather Joy Tollerud was born 2 March 1981.

bb. Erik Jon Tollerud was born 13 Dec 1983.

d. Gary Lee Pavlis was born on 28 July 1953.  He was married on 22 December 1974 to Mary Lynn Stephenson, born 17 Dec 1952.

aa. William Lee Pavlis was born 8 August 1979.  Married April Ganley, April 21, 2007

aaa. Jameson Alexander Pavlis was born November 17, 2010

bbb..  Aiden Killian Pavlis was born January 9, 2013

bb. Ann Marie Pavlis was born 20 May 1982.  Married Rob Lee June 2006, no children, Divorced, 2014, Married Luke Myers, May 2015

aaa.  Jack Laurence Myers, born April 5, 2016

bbb.  Hank David Myers, born July 11, 2019

cc. Katherine Jean Pavlis was born 4 August 1983, Married Keith Terlizzi, October 9, 2015

aaa. Breen Terlizzi, born April 8, 2017

bbb. Clara Rose Terlizzi, born April 13, 2019

e. Terry Lynn Pavlis was born 28 July 1953.  He was married on 8 Nov 1980 to Laura Serpa, born 21 July 1947.  

8. Agnes Pavlis was born in 20 Oct 1914.  She was married to William C. Williamson.  They divorced.  She died on 10 Feb 1995.  (Liver cancer, complication from hepatitis)  She lived much of her life in the Alliance, Ohio, area.

a. Darrell Williamson was born on 16 April 1950.  He married Nancy McFarlan.

aa. Ryan D. Williamson was born 16 Jan 1980.

bb. Elyse Williamson was born on 27 August 1985.

b. Cheryl Williamson was born on 23 April 1955.  She married Jerry Ziegler, divorced married Tim Stahr, and divorced again.

aa. Jeremy Ziegler was born 3 Jan 1977.

bb. Mandy Stahr was born 8 Feb 1986.

9. Margaret Pavlis was born 6 December 1917.  She died on 20 March 1995. She was married to Oliver Linnell.  She had Parkinson's disease for many years. They adopted two children.
			
a. Lee Linnell (adopted) was born on 15 April 1945.

b. Gene Linnell (adopted) was born in 1953.   

E. Annie Pavli\v{s} was born in 1870.  She died in 1957.  She married Albert Kole\v{c}ka who was born in 1868, he died in 1953.

1. Frank Kolecka married Elsie Phihal.

a. Edward Kolecka married Miss Beeson

aa. Debra Kolecka was a nun.

bb. Audry Kolecka

cc . Mavis Kolecka

dd. Sharon Kolecka

b. Vern Kolecka

c. Emil Kolecka 

2. James Kolecka never married.

3. Julia Kolecka married Frank Pavel.

a. George Pavel

b. Hattie Pavel

4. Rose Kolecka married Frank Kadelec

a. Irene Kadlec married Mr. Houska.

b. Viola Kadlec

c. JoAnn Kadlec married Mr. Verba

d. Barry Kadlec

5. John Kolecka married Alice Wentland in 1946.  

a. Betty Kolecka married Emil Gall

aa. Michael Gall

bb. Michelle Gall

b. Thomas Kolecka married Jean Odens

aa. Tracy Kolecka

bb. Tammy Kolecka

c. Anna Kolecka married Gary Uchytel.

a. Adam Uchytel

d. Eilene Kolecka married Terry Rasmussen

e. Richard Kolecka

f. Dianna Kolecka

6. Joseph Kolecka married Mavis Wentland

a. Donald Kolecka died  at an early age in a car accident.

b. Dorothy Kolecka married Mr. King.

a. Tony King

b. Koley King

c. Cheri King

d. Marty King.  

7. Mary Kolecka died at age 17.

F. Andrew Pavli\v{s} was born about 1867. In America he always spelled his name Pavlish.  He went to medical school in Kansas city and was graduated with an MD degree in 1901.  He was married, but they had no children.  He was run over by a truck at age 96 whilst he was getting the mail.

G. Vaclav Pavli\v{s} was born on 11 Feb 1875.  He died 14 Oct 1966.  He married Emilie Kucera.  They are buried in the Lake Andes Cemetary.    

1. Emil Milo Pavlis was born in 15 July 1902.  He died  1 Sept 1976.  He was married to Mary Novotny. She was born in 1900 and died in 1974.

2. Elsie Alice Pavlis was born 17 July 1903.  She died on 8 May 1988.  She was married to Emil Kucera.

3. Anton Wesley Pavlis was born on 3 April 1907.  He departed from this life on 11 April 1984.  He married Helen Slaba. Helen was Clara Slaba's sister, Clara was Tom Pavlis' wife. 

4. Albina Emma Pavlis was born on 24 May 1909.  She died on 22 June 1989. She was married to Henry Holleman.

a. Dolores Holleman was born on 11 Jan 1935.  She married William Klaut

aa. Kraig Klaut

bb. Kenton Klaut

b. Marlene Holleman was born 6 February 1937.  She married James Dahm born 29 Sept 1935.

aa. Jeffrey Dahm was born 17 November 1964. He married Sharon Byker, born 29 August 1963.

aaa. Jacob Dahm was born 14 December 1992.

bbb. Nicholas Dahm was born 14 August 1995.

bb. Jane Dahm was born 27 March 1967.  She married Timothy Rozendaal 17 Oct 1970. 

aaa. Justin Rozendaal was 26 August 1993.

cc. Sara Dahm was born 12 June 1973.  She married Charles DeGroat born 6 August 1970.

c. Harvey Holleman was bonr 10 October 1943.  He was married to Sandra Backens, they are divorced.

aa. Mary Beth Holleman was born 16 November 1972.

bb. Heide Holleman was born 10 April 1976.

5. Agnes Rose Pavlis was born 24 April 1914.  She was always known as Agnes, even though she was originally given the name Rose Agnes.  She married Ralph Engel who died in 1994.

	In 1995 Chad Pavlis received a call from Roy A. Davis, 414 Lingle Lane, Midland, Michigan 48640.  He had seen Chad's name in a Dow Chemical company personnelle listing, and was curious as to whether Chad might be a relative of his.  When information he had was compared with information about the Pavlis family in southern South Dakota, it was apparent that they almost certainly were relatives, because the name is extremely uncommon in the Czech republic and because the South Dakota Pavlis family and his had come from adjoining villages.  
	The  Roy Davis' ancestor Paul Pavli\v{s} was about the same age as Josef Pavli\v{s}, the oldest known ancestor of the South Dakota Pavlis family.   Perhaps Paul and Josef were brothers, born to a Pavli\v{s} who first fled Moslem persecution in Ottoman ruled Greece.  This outline is filled out on the  assumption that they were brothers. 

II. Paul Pavli\v{s} was born in what was then Bohemia in the Tabor area where Poli\v{c}ka is also located.  He had three children, the name of one is unknown.

A. Albert Pavli\v{s} was born in 1852 in the Tabor area.  He died 15 Dec 1920.  His first wife died in 1875.  He remarried Mary Fort, born 1865, died 1930.  

1. Bess Pavlis was born in 1875 and died in 1958.  Husband's name was Janecek.

2. Edward J. Pavlis was born 1 August 1885 and died 7 May 1941.  He was married in 1910 to Katherine E. Komrska, born 19 Mar 1885.  He worked for McCormick Deering making farm machinery and bicycles.  He moved to the farm after Albert died in 1920.  

a. Mildred Pavlis was married on 23 Nov 1939 to Clinton McPhall.

aa. Gary McPhall married Connie Cooper.

aaa. Carolyn McPhall married Leonard Piplinski
		
bbb. William McPhall 

ccc. Frederick McPhall

b. Elsie B Pavlis was born in 1912.  She was married on 28 Sept 1940 to Amil C. Norton, also born 1912. 

aa. Larry A. Norton married Judity A. Cunningham.  

3. Frank Nicholas Pavlis born 27 Nov 1887, died 14 June 1976.  He was married on 23 Nov 1915 to Anna Albie Zalud, born 4 July 1894, died 27 Nov 1970.  

a. Frank Edward Pavlis was born 29 Oct 1916.  He married Ethel Piel. He was the engineer who developed the system for nitrogen liquification used by Air Products and was one of the founders of that company.

b. Elmer Albert Pavlis was born 19 Nov 1918.  He was married on 16 Nov 1943 to Dorothy Mae Kroupa, born 11 Sept 1914.  He is responsible for the existence of a wonderful museum in Michigan.

aa. Vivian Marie Pavlis was born 23 Oct 1943.  She married a man named Steinbauer.

aaa. David Marcus Steinbauer was born 5 July 1976.

bbb. Sarah Elizabeth Steingauber was born 22 Sept 1979.

bb. James Frank Pavlis was born 12 December 1947.

cc. Jean Ann Pavlis was born 21 April 1951.  She married Mike English.  

c. Agnes Mae Pavlis was born 27 Sept She was married on 28 November 1942 to Ervin Davis.  

aa.  Paul Richard Davis

bb. Roy Allan Davis was born 17 Oct 1950.  He was married on 20 April 1972 to Colleen Sue Chandler.  

aaa. Jonathan Davis. 

2. Alba Pavlis born 19 Sept 1892, died 30 Sept 1966.    

B. John Pavlis lived in the old Pilsen District of chicago.  

1. John Pavlis was born 18 May 1882 and died 25 August 1885.

2. Anna Pavlis was born on 23 July 1884 and died 24 Dec 1918.  She married Martin Pitner (that is the way it is spelled in records, family always spelled it Pittner).  When Anna died, he married her sister Emma.  Marriage was April 1904.  He was a baker.  

aa. John James Pittner was born on 4 July 1904 in Chicago.

bb. Joseph Pittner was born on 24 March 1909 in Chicago.

cc. George Pittner was born on 5 October 1907 and died 30 Jul7y 1976.

3. Rose Pavlis was born on 238 August 1886 and died 27 April 1938.  She married William Doubek, born 15 Jan 1885 in Chicago.  William was a police Custodian in Chicago.  

a. Bohumil Doubek was born 5 November 1908, and died 28 December 1955.  He married Margaret.  He was an accountant.

aa. William Doubek

bb. Joan Doubek who married Mr. McGowan.

4. Bohumil Pavlis was born on 28 Nov 1888.  He died in the 1970's. He married Lillian Zajicek.  

a. Edward Pavlis was born 14 October 1911.  

5. Emma Pavlis was born on 21 June 1891 and died 2 October 1924.  She married Martin Pitner after Anna died.  He drank too much and shot her too death. They were married in 1923, only about a year before he killed her.  He was not sent to prison, and remarried another woman, Magdelena Cepak.  

6. Mary Pavlis was born 17 October 1893 and died 5 Jan 1960.She married James Reznicek.

a. Richard Reznicek, born 24 August 1919.  He married Dolores

b. Eleanore Rezincek was born 7 Oct 1914.  She married Roy Hegar, accountant.

7. Josephine Pavlis was born 7 June 1896.  She married Joseph Cuchna, born 1893.  

a. Violette Cuychna was born on 29 Jan 1916 in Chicago.  She married Raymond Mokolas in 1938.

aa. Nancy Mikolas.

bb. Cynthia Mikolas.

8. Joseph Pavlis was born 20 Jan 1899 and died 14 march 1925.

9. Ludmila Pavlis was born 24 April 1903 and died 8 December 1906.  

\vskip 4mm
End of Pavlis family
\pagebreak

{\noindent \Huge \bf Bogenhagen Family}
\vskip 6mm
	Wilhelm Friedrich August Bogenhagen was born on 22 March 1822.  He married Ernestine Louisa who was born on 8 July 1822.  Wilhelm died on 5 June 1888 in Germany, and Ernestine died on the 7 October 1874, also in Germany.  Wilhelm had three sons, all were born in Benz Kreis Kammin, Stetin, Pomerania.   Two of the sons, August and Friedrich travelled to America where they spent the rest of their lives. Wilhelm remained in the Stetin area until his death.

I. August Friedrich Wilhelm Bogenhagen was born on the 29th of February in 1848 and died on 28 February 1910 in Osmond, Nebraska.  He married Ernestine Wilhelmine Zulksdorf  (born 20 June 1853 at Welschenburg Kr. Dramburg, died in April of 1919 of Smallpox.)  August and Ernestine were married in Germany.  

A. William Friedrick Adolf Bogenhagen was born on 25 December 1877 in Germany. He died in Sedgwick, Colorado, on 14 December 1950.  He was married twice, first wife Millie Mohr was born 5 August 1878, and died 20 December 1907.  He remarried in a few months to  Katherine Schmidt who was born on 22 January 1884 in Flensburg, Germany. She died 19 February 1970 in Englewood, Colorado.
		
1. Valeria Zenobia Bogenhagen was born 20 August 1904 in Osmond Nebraska (wife 1) she was married on the 25th of July to Joseph Edward Deranleau (born 30 Dec 1900 in Montana, died 11 July 1963.)

2. August William Bogenhagen was born on 26 April 1910 in Bloomfield, Nebraska.  He married Dixie Shelly who was born on 1 October 1910 in Tennessee and died on 13 July 1960.  Marriage date: 15 December 1946.

3. Severa Junita Bogenhagen was born on 22 August 1911 in Bloomfield, Neb. On 27 August 1934 she married Randyll Sylvester Froid (born 9 June 1908 in Colorado, died 15 March 1976.)  

a. William Charles Bogenhagen was born 17 September 1935 in Greely, Colorado.  On 22 September 1956 he married Ann Gager, born 3 Feb 1938 in Denver, Colorado.
		
aa. Brian Charles Bogenhagen was born 4 July 1958.  He married Denise Marchia Segelke on 23 Feb 1980.

aaa. Joshua Adam Bogenhagen was born 6 Aug 1979.

bbb. Jacob Randall Bogenhagen was born 1 Oct 1981.

bb. Wendy Lee Bogenhagen was born 30 January 1961 in Brighton
				
aaa. Nicole was born 26 July 1981.

cc. Lisa Ann Bogenhagen was born 5 December 1965 in Denver.

b. Beverly Jean Bogenhagen was born on 20 November 1937 in Greely. She was married on 10 July 1964 to John Siegfried Welsh who was born on 23 April 1938 in Spokane, Washington.
				
aa. Tammy Lynn Welsh was born 13 June 1966 in Spokane,Wash.

bb. Sherry Kay Welsh was born 27 August 1967 in Denver.

c. Betty Ann Bogenhagen was born 31 Jan 1941.  On 14 Jan 1964 she married Charles William Lemons who was born 11 December 1942 in Ill. On 17 September  1975 she remarried Fred Winkinhofer.

aa. Daniel Wayne Lemons was born 1 March 1965.

bb. David Allen Lemons was born 2 December 1975.

3. Lester Herbert Bogenhagen was born on 10 July 1913.  On 4 August 1934 he married Oma Fae Fisher who was born on 4 August 1915 in Sedgwick, Colo.

a. Janet Ruth Bogenhagen was born on 14 March 1935 in Sedgwick. She was married on 1 January 1957 to Robert Charles Lindsay, who was born 11 December 1932 in Peetz, Colorado.
 
aa. Jonna Lee Lindsay was born 24 April 1959 in Denver and on 14 Mar 1980 married Forest Dale York, born 16 Jan 1956.
			
bb.  Jeffrey Howard Lindsay was born on 14 March 1961 in Denver.  On 12 Sept 1981 he married Kristelle Kay Eitel who was born 19 June 1962.

cc. James Lester Lindsay was born 13 October 1962 in Denver.

b. Joanne Frances Bogenhagen was born on 3 Sept 1936 in Sedgwick. She was married on 22 March 1958 to Kent Homer Lizar who was born in Denver on 7 July 1932.

aa. Francis Ann Lizar was born 25 Feb 1959 in Denver.

bb. Melody Lynn Lizar was born 1 Mar 1961 in Denver.

cc. Jodene Rae Lizar was born on 10 July 1963 in Denver.
		
c. Barbara Ann Bogenhagen was born on 27 October 1937 in Sedgwick. She was married on 12 September 1959 to Charles Adam Schell who was born 18 December 1937 in Sterling, Colorado.

aa. Cynthia Lee Schell was born 5 May 1961 in Denver.  She was married on 11 Ap 1980 to Jeffrey Kenneth Konegni who was born 18 October 1960.

aaa. Michael Kenneth Konegni was born on 16 May 1981.

bb. Linda Sue Schell was born on 15 Sept 1963 in Denver.

cc. Scott Charles Schell was born on 25 Feb 1967 in Englewood.

B. Gustave Adolph Helimoth Bogenhagen was born on 2 August 1880 in Munchendorf, Germany.  He died 15 November 1954 in Cheyenne Wells, Colorado.  On 8 August 1909 he married Olive Lillian Brown who was born on 5 May 1885 and died 1 July 1969.

1. Ardis Bogenhagen was born on 22 April 1912 in Beemer, Nebraska.  She was married on 27 June 1931 to Harold Froelich .

2. Anita Bogenhagen was born on 18 December 1914 in Beemer, Nebraska.  She was married to Tom Price on 24 June 1935.  He was born on 29 Oct 1898.

a. Buckley Price was born on 29 November 1936 in Palmdale, Ca.  He died in the military on 1 July 1959.

b. Anita Price was born on 25 March 1942 in Goodland, Kansas.  She married Gary Oliver 9 September 1965.  Mr. Oliver was born on 26 July 1942.

aa. Tonya Oliver was born on 13 March 1971.

c. Jim Price was born on 2 May 1944 in Boulder, Colorado.

d. Patricia Price was born on 14 June 1948 in Boulder. She was married on 7 December 1967 to Max Norwood who was born on 12 May 1943.

aa. Brett Norwood was born on 18 Jan 1970.

bb. Jeffery Norwood was born on 28 Jan 1972.

e. Terry Price was born on 15 October 1949.  He was married on 1 August to Debbie.

aa. Stacy Price was born in 1973.

bb. Chris Price was born on 6 June 1977.

3. Lyle Oris Bogenhagen was born on 11 November 1918 in Julesburg.  He married Ada Comma, born 30 May 1926.  Wedding date: 11 Dec 1949 at Ancona, Italy.

a. Andy Bogenhagen was born on 15 September 1950 in Colorado.

b. Giovanna Bogenhagen was born 30 March 1953. She was married on 26 June 1976 to Doug Gellatly.

aa. Paul Raymond Gellatly was born 12 February 1979.

bb. Angelia Maria Gellatly was born 24 October 1981.

c. Charles Bogenhagen was born 20 September 1955 in Colorado.

d. Elizabeth Bogenhagen was born 27 June 1963.

(All four of the above were born in Cheyenne Wells, Colorado).

4. Iola Grace Bogenhagen was born 27 February 1920 in Julesburg.  On 1 March 1937 she was married to Roy William McCormack who was born on  9 Dec 1913.

a. Neva Mae McCormack was born 9 September 1938. She was married on 19 August 1956 to Gary Marten Toet, born 31 July 1937.

aa. Kenneth Wayne Toet was born 27 June 1958.  On 10 Jan 1981 he married Victoria Carol Vance.

bb. Cynthia Lee Toet was born 25 April 1961.  She was married on29 November 1981 to David Wilson.

cc. Gregory Martin Toet was born 23 Jun 1965.

b. Melvin Roy McCormack was born 26 August 1940.  He was married on 28 April 1962 to Sharon Lorraine Harvey born 4 March 1945.

aa. David Charles McCormack was born 8 October 1964.

bb. Peggie Michele McCormack was born 16 September 1966.

cc. Charlene Carol McCormack was born 16 July 1969.

dd. Leah Eilene McCormack was born 31 Jan 1972.

ee. Susan Lorraine McCormack was born 20 March 1974.

c. Betty Ann McCormack was born 24 May 1943.  She was married on 28 April 1962 to Daniel Earl DuRocher, born 24 June 1941.  Betty divorced and remarried Fritz Hugh Lee. She divorced again and remarried Wayne Ireland Gilbert. 

aa. Danette Marie DuRocher was born 13 Feb 1961.

bb. Kimberly Lynn DuRocher was born 10 March 1962.

cc. Brenda Moria Lee was born 21 December 1967.

dd. Tanna Diana Lee was born 9 July 1969.

ee. Anthony Gilbert was born 7 March 1975.

5. Neva Bogenhagen was born 24 Jan 1922 in Cheynne Wells, Colorado.  She was married to Ben Liefermann, born 4 March 1911, died 11 December 1971. Her children were all born at Cheyenne Wells, Co.

a. Arlene Leiferman was born 9 March 1945.  She was married 3 Jun 1965 to Tim Rockwell, born 1 Feb 1946.

aa: Shellie Rockwell was born 15 Jan 1966 at Moab, Utah.

bb. Todd Rockwell was born 23 November 1969 at Las Vegas.

b. William Leifermann was born on 11 December 1949.

c. Doris Leifermann was born 13 January 1952.  She was married on 30 March 1974 to Gary Epperson, born 13 August 1946. 

aa. Heath Epperson was born 13 May 1976 at Cheyenne Wells, Co.

bb. Luke Epperson was born 11 Jan 1980 at Gordon Nevada.

6. Gayle Howard Bogenhagen was born 23 August 1926 at Cheyenne Wells, Colo.  He was married on 13 December 1945 to Dorene Oglesby. 

a. Gary Lynn Bogenhagen was born on 4 Dec 1946. He was married on  23 May 1968 to Bonnie Musch, born 12 November 1950. 

aa. Sonia Renee Bogenhagen was born 8 Sept 1968.

bb. James Bradley Bogenhagen was born 23 October 1969. 

cc. Jill Allison Bogenhagen was born 21 August 1974.

dd. Aaron Shawn Bogenhagen was born 24 April 1978.
			
b. Gene Howard Bogenhagen was born 21 Oct 1948.  He was married on 20 August 1970 to Nancy Escudero, born 18 August 1951.

aa. Chad Howard Bogenhagen was born 9 Jan 1973.

bb. Brandie Dawn Bogenhagen was born 13 Feb 1975.

cc. Julie Marie Bogenhagen was born 23 September 1977.

dd. Holly Jean Bogenhagen was born 2 January 1979.

c. Donna Sue Bogenhagen was born 18 February 1952.  She was married on 27 March 1976 to Jerry Hoss, born 28 February 1952.

aa. Nicole Ann Hoss was born 7 October 1977.

bb. Jeff Scott Hoss was born 6 April 1979.

d. Paula Ann Bogenhagen was a twin.  She was born on 5 February 1953. She was married on 22 July 1972 to Ronald Hollenbaugh, born 8 Jan 1951.

aa. Jennifer Jo Hollenbaugh was born 6 February 1975.

bb. Timothy Ronald Hollenbaugh was born 26 Septenmber 1977.
		
e. Paul Alan Bogenhagen was Paula's twin.  He was born on 5 February 1953.  He married Rebecca Schaeffer on 2 March 1974.  They divorced.

aa. Christopher Paul Bogenhagen was born 8 September 1974.

bb. Todd Alan Bogenhagen was born 30 Oct 1977.

f. Barry Wayne Bogenhagen was born 16 March 1959.  He married Michele Beeson on 4 March 1978.  They quickly divorced.

aa. Casey Wayne Bogenhagen was born 14 May 1978.

g. Calvin Ray Bogenhagen was born 23 February 1961.  He was married on 24 October 1981 to Suzanne Johnson, born 28 July 1964. 

aa. Jeremiah Johnson Bogenhagen was born 3 May 1982.

C.  Clara Hedwig Agnes Bogenhagen was born 10 January 1883 and died on 19 October 1938 in Osmond, Nebraska.  She married M. T. Liewer on 28 June 1908.  He was born 12 Nov 1875 Carrol, Iowa, and died 2 May 1971 in Lincoln, Nebraska.

1. Paul Liewer's birth date is not known to these authors.  He was married on12 November 1935 to Gertrude.

a. Paul T. Liewer was born on 3 March 1943.  He married Becky Hansen.

aa. June Liewer

b. James A. Liewer was born 26 Jan 1945.  He became a priest, once served at Risen Christ Cathedral, Lincoln.

c. Peggy A. Liewer was born 12 October 1946.  Nun: Sister Ann Maureen.

2. Eugene M Liewer was born on 28 December 1911.  He was married on 22 January 1935 to Louise Schmitz.

a. Donald E. Liewer was born 23 July 1935.  He was married on 23 November 1956 to Gail S. Clough, born 31 March 1938.

aa. Patricia Ann Liewer wasw born 10 September 1957.

bb. Steven Bruce Liewer was born 8 Feb 1961.

cc. Joan Maria Liewer was born 8 April 1965.

dd. Scott Donald Liewer was born 26 July 1967.

b. Anita Louise Liewer was born 4 February 1938.  She married Gary Morrell, born 10 March 1938.

aa. Mitchell Jon Morrell was born 11 November 1961.

bb. Kyle David Morrell was born 5 April 1963, died in 1975.

cc. Desieree Michelle Morrell was born 17 April 1964.

dd. Jacqueline Marie Liewer was born 5 October 1965.

c. Mary Jane Liewer was born 11 July 1940.  She was married on 20 Jan 1962 to Duane Weber, born 10 Jan 1940.

aa. Tonya Rae Weber was born 27 February 1968.

bb. Timothy Duane Weber was born 25 April 1970.

d. Gloria Jean Liewer was born 6 October 1944.  She was married on 9 July 1966 to William Duenwald, born 9 November 1942.

aa. Kimberly Kay Duenwald was born 8 September 1967.

bb. Thomas Matthew Duenwald was born 18 September 1968.

cc. Molly Elizabeth Duenwald.

3. Ralph J. Liewer was born 16 February 1914.  He was married on 6 Feb 1942 to Mary Lurette Hansen.

a. Kurt Matthew Liewer was born on 9 June 1945.  He was married on 25 January 1969 to Paula Eva Creyke, born 27 June 1945.

4. Francis Elmo Liewer was born 10 December 1914.  He was married on 23 Jan 1943 to Elizabeth Rose Arduser, born 4 February 1922.

a. Karl Daniel Liewer was born 19 February 1944.

b. Steven Robert Liewer was born 7 May 1946.

c. Elizabeth Ann Liewer was born 22 May 1947.  She was married on 2 September 1967 to Stephen Henry Borgmann, born 27 June 1945.

aa. Melissa Borgmann was born 8 November 1968.

bb. Benjamin Borgmann was born 30 December 1969.

d. David Francis Liewer was born 12 September 1948.

e. Timothy Mathias Liewer was born on 15 April  1951.  He was married on 27 November 1970 to Donita Diane Dvorak, born 24 May 1951.
 
aa. Choan David Liewer was born 27 May 1971.

f. Michael Dale Liewer was born 8 May 1955.

g. Joseph Don Liewer was born 2 April 1965.

5. Karl R. Liewer was born 2 July 1924.  He was married on 22 August 1975 to Ellen Moroney, born in 1929.  He was graduated from West Point.    

D. Minne Clara Amanda Bogenhagen was born 7 October 1884 at White Lake, S.D.  She died 30 Mar 1967 in Osmond, Nebraska.  On 25 December 1903 she married Edwin Weingartner who was born 19 August 1873 and died 18 April 1947.

1. Flora Alma Weingartner was born on 28 October 1904 in Osmond, Nebraska.

2. Verna Estella Weingartner was born on 22 June 1907 in Osmond, Nebraska. She died on 26 June 1978 in Omaha.

3. Velma Edna Weingartner was born on 2 June 1909 in Osmond.  On 16 March1940 she was married to Ralph Leslie Norris, born 6 July 1912, died 4 Feb 1958.

a. Allan Edward Norris was born 4 December 1940.  He was married on 28 August 1960 to Lois Marie Petersen.  Their children were all born in Norfolk, Nebraska.

aa. Clifford Allan Norris was born 26 April 1963.

bb. Dean Leon Norris was born 18 August 1968.

cc. Scott Ralph Norris was born 19 May 1970.

b. Larry Lowell Norris was  born 10 May 1943 in Plainview, Nebraska. He was married 21 July 1968 to Sarah Abigail Mangan who was born 23 June 1943.

c. Ronald Ralph Norris was born 5 September in Plainview, Neb. He was married on 17 September 1967 to Nancy Ellen Walmsby, born 4 October 1943 at Norfolk.  The children were born in Plainview, Nebraska.

aa. Janet Ellen Norris was born 7 August 1968.

bb. Michael Ronald Norris was born 29 June 1970.

4. Harold Edwin Weingartner was born 6 September 1911 in Osmond, Nebraska. He was married on 21 November 1943 to Dorothy Jackson.

5. Lowell Charles Weingartner was born 4 April 1915 in Osmond and died 15 August 1941 at Norfolk, Nebraska.

6. Alice Ilene Weingartner was born 15 December 1921 at Osmond, Nebraska. She was married on 3 April 1949 to Orpheus Raymond Erwin, born 24 Jul 1916.

a. Cheryl Rae Erwin was born 2 March 1951 at Osmond.  She was married on 25 September 1971 to Edward Wattier, born 20 January 1950. She was divorced in 1979.

aa. Rhonda Ann Wattier was born 6 March 1972.

b. Rodney Lee Erwin was born 8 August 1952 in Osmond.  He was married 8 April 1978 to Rhonda Kay Hagge, born 11 Nov 1956.

aa. Chad Rodney Erwin was born 1 Jan 1980 at Dallas, Tx.

bb. Audra Kay Erwin was born 16 Jan 1982 at Osmond.

c. Robert Dean Erwin was born 1 March 1956 at Osmond. On 7 Oct 1978 he married Jean Kumm, born 2 January 1969 Osmond.

aa. Travis Ryan Erwin was born 5 May 1980.

7. Janice Mae Weingartner was born 4 December 1925 in Osmond.  She was married on 29 October 1945 to Bryl Waverly Luttman, born 4 Dec 1920.
 
a. Patricia Jeane Luttman was born 29 December 1946 at Osmond. She was married 22 February 1969 to Ronald James Deermer, born 4 November 1946 at Atkinson, Nebraska.
 
aa. John James Deermer was born 29 July 1969, Norfolk.

bb. Deborah Jeanne Deermer was born 14 March 1972.  She was stabbed to death on a U.S. army base on 22 April 1980.

cc. David James Deermer was born 26 January 1977.

b. Pamela Ann Luttman was born 17 July 1948 in Norfolk.  She was married on 27 June 1971 to Dr. Gary Lynn Rademacher, born 4 December 1946 at Loup City, Nebraska. All of their children were born in Nebraska City, Nebraska.

aa. Mary Pamela Rademacher was born 11 August 1974.

bb. Ann Lynn Rademacher was born 8 February 1976.

cc. Beth Lee Rademacher was born 13 Jan 1978.

dd. Adam Earl Rademacher was born 5 May 1981.

E. Anna Amanda Augusta Bogenhagen was born 27 April 1886 at White Lake, S.D.  She died on 2 October 1976 in Fort Collins, Colorado.  On 27 November 1912 in Niobrara, Neb, she married George Washington Draper, born 22 February 1883, Niobrara, who died 19 January 1969.

1. George Woodrow Draper was born 2 September 1913.  He was married on9 May 1958 at Raton, New Mexico, to Lydia Helzer Manning.

2. Wayne Pershing Draper was born 4 November 1918.  He was married on 3 Jan 1948 in Milwaukee Wisconsin to Jean Rololl.
 
a. Michael John Draper was born on 26 November 1948.

b. Jennifer Susan Draper was born 16 July 1951.

c. James Woodrow Draper was born 15 October 1952.

F. August Fredrick William Bogenhagen was born on 9 April 1888 at White Lake, SD. He died 4 March 1933 in Denver.  On 24 February 1917 at Pierce, Nebraska, he married Stella Docken who was born on 31 March 1897 and died 31 July 1966.

1. Marlon Lee Bogenhagen was born 28 July 1918.  He died 27 February 1967. He was married on 1 June 1942 to LaVara Bolen.
 
a. Evelyn Caryl Bogenhagen was born 30 March 1943.  She married Kenneth Thompson, born 25 March 1937, on 3 June 1963.
 
aa. Darren Todd Thompson was born 28 Jan 1966.

bb. Michelle Lynn Thompson was born 23 Oct 1967.

b. Linda Nell Bogenhagen was born 13 Jun 1945.  She was married on 6 December 1969 to Joe Vester, born 7 August 1945.  
 
aa. Chad Bryan Vester was born 18 Jan 1973.

bb. Sandra Kay Vester was born 17 August 1975.

2. Joyce Elwood Bogenhagen was born in August of 1920.  She died in a bicycle accident in August of 1933.

3. Leslie August Bogenhagen was born 2 June 1922.  He was married on 29 May 1946 to Thelma Nootz, born 31 October 1923. 

a. William Leslie Bogenhagen was born 14 March 1947.  He was married on 17 August 1968 to Theodora Sponsel, born 3 November 1949.
 
aa. Nichole Danyelle Bogenhagen was born 19 August 1978.

b. Larry Lee Bogenhagen was born 22 April 1949.  He was married on 23 June 1970 to Estrelita Alea, born 3 Nov 1943 in the Philippines.

aa. Ley Ryan Ashley Bogenhagen was born 15 Jan 1974.

c. Lorraine Yvonne Bogenhagen was born 15 December 1955.  She was married on 28 October 975 to Jimmy Gardner, born 30 Sept 1950. They later divorced.
 
4. Orville James Bogenhagen was born 18 March 1924.  He was married on 9 April 1944 to Sylvia Anderson, born 7 December 1924.
 
a. Edith Marie Bogenhagen was born 2 Jan 1946.  She was married to Glenn Brown on 30 October 1965.  He was born on 19 Aug 1946.

aa. Tana Marie Brown was born 19 Sept 1967.

bb. Jeffrey Allen Brown was born 3 November 1969.

b. Bette Ann Bogenhagen was born  21 Feb 1949.  She married Greg Culjar, born 5 Oct 1947.  They later divorced.

aa. Deenna Marie and Rachel Ann Culjar were born 3 Feb 1970.

c. Dennis Orville Bogenhagen was born 5 March 1947.  He married Diane Krumbholz, born 21 Feb 1948.  They later divorced.
 
aa. Lindsey Deanne Bogenhagen was born 11 May 1970.

5. LeWayne Marshall Bogenhagen was born 19 October 1932.  He was married on 16 Feb 1955 to Marilyn Ann Hicks, born 12 June 1934.
 
a. Michael Lewayne Bogenhagen was born 9 October 1955.

b. Colleen Sue Bogenhagen was born 28 March 1958.

c. Mark James Bogenhagen was born 31 December 1961.

d. Shawn Eric Bogenhagen was born 15 November 1963.  

G. Alma Augusta Emilie Bogenhagen was born on 21 Nov 1890 in Osmond, Nebraska. She died on 17 July 1968 in Julesburg, Colorado.  She married Walter Herman Junge (born 27 Nov 1892 in Osmond, died 25 June 1969, Julesburg Colorado.) Wedding date: 11 May 1915.

1. Walter DeWayne Junge was born 26 September 1920 in Big Springs, Neb. He died 4 April 1964.	He married Ethel Anna Rahe on 6 August 1942.  She was born 8 Dec 1920 Hays, Kansas.

a. Pamela Kay Junge was born 25 April 1943 in Sidney, Nebraska.  She was married on 17 September 1961, to Charles Gene Sturgis, then divorced, and married, on 15 Sept 1977, Dr. Lloyd E. Sedgwick, born1 Jan 1937, Brooklyn New York.

aa. Charles Rahe Sturgis was born 1 August 1969 in Denver

bb. Tami Daniel Sturgis was born 27 April 1971 in Denver.

b. Walter Rahe Junge was born 24 October 1944 in Sidney, Nebraska.  He was married on 4 February 1965 to Cheryll Ann Crest, born 11 October 1944.
  
aa. Brad Herbert Junge was born 23 June 1966 in Denver.

bb. Alycia Lee Junge was born 24 July 1967 in Tyler, Texas.

2.  Robert Stanley Junge was born 20 June 1923 in Big Springs, Nebraska.  He became a dentist.  On 31 August 1952 he married Addie May Hunter, born 22 March 1920.
 
a. Mitchell Kent Junge was born 22 January 1954, and married on 4 August 1979 to Karin Rose Kunkell, born 2 April 1956.
 
b. Barbara Alice Junge was born 28 May 1955 in Denver.

c. Robert Hunter Junge was born 13 January 1959 in Denver.

3. Marshall F. Junge was born 16 October 1924 in Big Springs, Nebraska.  On 4 April 1947 he married Roberta Anne Johnson, born 3 April 1927 Ft. Collins.

a. Dennis Michael Junge was born 30 June 1949 in Fort Collins.  He was married on 16 June 1971 ro Pamela Redding, born 24 January 1950 at Colorado Springs.

aa. Elisa Christine Junge was born 27 September 1973, Norfolk, Virginia.
 
bb. Heide Elizabeth Junge was born 27 Apr 1977 Monterey, Calif.

cc. Laura Alexis Junge was born 15 Feb 1979, Annapolis, Md.

b. Kenneth Brent Junge was born 2 Oct 1952 in Fort Collins, Colorado. He was married 17 December 1972 to Janice Marie Anderson, born17 March 1953 at Colorado Springs.

aa. Mathew Barrett Junge was born 15 March 1977 in Phoenix.

bb . Karen Michelle Junge was born 19 Jan 1980  in Boise.
				
cc. Daniel Brian Junge was born 5 June 1982 in Boise.

c. Marsha Anne Junge was born 21 August 1956 in Colorado Springs. She was married on 26 August 1978 to Dwight Whittend, born 14 December 1950 in North Dakota.

aa.  Sarah Anne Whittend was born 5 June 1982, Colo Spgs.

H. Harriet Hertha Ernestine Bogenhagen was born 3 October 1894 in Osmond Nebraska. She died in Florida on 22 August 1979.  She was married on 21 June 1916 to Richard Travis Elliot (born 21 September 1889, Aberdeen, S.D. died 11 Jun 1943 Westport, Connecticut.)

1. Richard Travis Elliot was born 11 Jan 1918 and died 2 June 1920.

2. Herschell Hugh Elliot was born 6 Feb 1920 in Bloomfield, Connecticut.

3. Ruth Adelaide Elliot was born 9 September 1923 in North Haven, Connecticut. She was married on 4 June 1948 to James David Andrews.
 
a. David Graham Andrews was born 8 December 1950.

b. Elizabeth Lindsey Andrews was born 12 Feb 1953.

c. Richard Elliot Andrews was born 8 November 1956.

d. Holly Andrews was born 9 October 1959.

e. Ruth Eleanor Andrews was born 5 May 1962.

4. Paula Ann Elliot was born 11 October 1924.  on 4 August 1947 she married William L. Bradley.

a. James Richard Bradley was born 11 September 1950.

b. Dwight Culver Bradley was born 11 February 1952.  He is in geological sciences,  knew Terry Pavlis for years without recognising that they were relatives!

c. Paul William Bradley was born 11 September 1954.

5. David B. Elliot was born 23 July 1927.  He was married in December of 1959 to Anna Belle Connelly.

a. Patrick David Elliot was born 13 March 1961 in Hudson, NH.

b. Patrick David Elliot was born 27 September 1962 in Seattle.

c. Bradley Andrew Elliot was born 21 May 1969.

II. Fredrick Wilhelm Bogenhagen was born 6 January 1850.  He died on 26 October 1916. One source said that he died of prostate cancer, another colon cancer.  He was married on 26 April 1873 to Augusta Theresa Jasch, born 21 November 1856, died 13 September 1939.  Their first five children were born in Cook County, Illinois, the last five in Aurora County, South Dakota.

A. William August Bogenhagen was born 3 November 1874 and died on 4 February 1961.  	He was married on 4 May 1899 to Anna Maria Lemcke, born 21 May 1876, died 20 July 1906.

1. Elsa Bogenhagen was born on 9 July 1900 and died shortly after birth.

2. Alma Johanna Fredericka was born on 1 September 1901. She died in 1986. She was married on 5 June 1952 to Herbert Frederick Matzner who was born on 3 November 1918 and who died 5 December 1955.

3. Carl Johann Bogenhagen was born on 14 July 1904 and died about a year later.

4. Elfride Bertha Bogenhagen was born 28 April 1906 and died 1 Feb 1979.  She was married on 9 June 1931 to Fred Horst who was born 2 April 1899 and who died 30 December 1973.

a. Joann Helen Horst was born 15 May 1933.  She was married on 8 Jan1955 to Duane William Zeisler born 18 Feb 1933.

aa. Jane Sue Zeisler was born 5 June 1957.  She was married on 9 June 1979 to Richard Schmitz.

aaa. Ryan Lee Schmitz.

bb. Craig William Zeisler was born 7 March 1959.

cc. James Duane Zeisler was born 9 January 1963.

b. Ardyce Ann Horst was born 15 April 1936.  She was married on 15 June1963 to Richard Nelson, born 2 June 1940.  They were divorced.  She was remarried on 28 September 1996 to Herbert Struss.

aa. Tyler Nathen Charles Nelson  was born 6 May 1964.

bb. Stacy Marie Nelson was born 27 December 1966.

cc. Sara Rene Nelson was born 24 September 1969.

c. Judy Carolyn Horst was born 22 July 1940.  She was married on 3 September 1966 to Robert Anderson, born 11 Oct 1940.

aa. Robert Alan Anderson was born 5 Feb 1971.

bb. Brice Eli Anderson was born 27 April 1973.

d. Lorna Alice Horst was born 23 February 1942.  She was married on 10 December 1965 to Leonard Dean Thomas, born 16 Sept 1940.

aa. Jeffrey Dean Thomas was born 18 Feb 1968.

bb. Tiffany Lynn Thomas was born 13 June 1972.

cc. Jeremy Fredrick Thomas was born 27 September 1978.

dd. Danita Kay Thomas was born 26 January 1980.

e. Shirley Jean Horst was born 29 Apri 1946.  She was married 22 August 1965 to Wayne Allen Keizer, born 10 July 1945.

aa. Tonya Renee Keizer was born 24 June 1967. She married Jeffrey Zinter.
				 
aaa. Caitlin Zinter was born in June 1991. 

bb. Lance Fredrick Keizer was born 5 May 1971.

cc. Forrest Conrad Keizer was born 17 June 1974.

B. August Bogenhagen was born on 16 August 1876 and died on 23 September 1915. He was married in 1906 to Clara Ingelthrone, born 6 December 1882, died 25 June 1980.  They adopted a son Louis Edwin was born 15 November 1908.

C. Amanda Bogenhagen was born 12 August 1978, died of thyroid cancer 13 February 1949.  She was married in April of 1907 to Herman Miller, born 27 Nov 1864, died 27 Feb 1951.

1. Alvina Augusta Miller was born 8 January 1908 and died 16 March 1960.  She was married on 8 January 1929 to Richard William Clark, born 23 April 1901, died 7 March 1964.

a. Elaine Alvina Clark was born 17 August 1931.  She was married on 11 June 1950 to William Eurgen Hoffman, born 11 Nov 1928.

aa. Bruce William Hoffman was born 1 May 1952.  He was married on 24 November 1979 to Cheryl Ehrich born 27 May 1958.

bb. Suzan Marie Hoffman was born 24 September 1959.

cc. Lorri Ann Hoffman was born 21 July 1961.

b. Donald Edward Clark was born 23 October 1929.  He was married on 9 June 1952 to Lorraine Sanger born 3 November 1929.
 
aa. Craig Clark was born 25 April 1956.  He was married on 8 April 1978 to Megan, born 9 June 1956.
				
bb. Mary Beth Clark was born 13 May 1962.

2. Hermann Miller was born 21 November 1910. He died 5 August 1989. He was married on 6 October 1940 to Muriel Taylor, born 8 June 1919.

a. Marlene Miller was born 23 March 1943.  She was married on 8 June 1961 to Ronald Dodd, born 6 November 1941.

aa. Robin Dodd was born 9 September 1960.

bb. Brad Lee Dodd was born 14 October 1966.

b. David Miller was born 17 September 1945.  He was married on 12 July 1968 to Cheryl Goetfert, born 23 March 1946.

aa. Carey Ann Miller was born 18 June 1975.

bb. Camey Lyn Miller was born 9 June 1977.

3. Walter Carl Miller was bon 21 January 1913.  He was married on 28 Dec 1939 to Margaret Blanche Knox.

a. Walter Richard Miller was born on 3 May 1941.  He was married on 24 September 1977 to Ann Armond, born 22 December 1941.

aa. Marcus Richard Miller was born 9 March 1965.

bb. Solimar Miller was born 12 December 1969.

b. Ronald Knox Miller was born 10 August 1943 and was married on 4 June 1965 to Trisha Leavitt, born 28 November 1942.

aa. Aaron Leavit Miller was born 19 March 1974.

bb. Chandra Kathryn Miller was born 3 September 1971.

cc. Adria Miller was born 10 March 1969.

c. Carl Herman Miller was born 19 October 1947.  He was married on 15 July 1972 to Mere McCamish, born 3 January 1950.

aa. David Miller was born 5 Feb 1974.

bb. Becky Margaret Miller was born 17 October 1977.

d. Robert William Miller was born 7 May 1951.  He was married on 20 November 1977 to Martha Othon, born 12 April 1952.
 
aa.  Kristy Ann Miller was born 10 Feb 1980.

4. Arnold Albert Henry Miller was born 23 February 1915.  He was married on 6 October 1940 to Ester Karen Marie Sorenson, born 31 August 1917.

a. Karen Marie Miller was born on 16 June 1943.  She was married on 21 November 1964 to Ronald Weich, born 10 October 1941.
 
aa. Troy Ronald Weich was born 5 July 1966.

bb. Kristen Weich was born 20 May 1968.

b. Kathlene Rae Miller  was born 15 November 1946.  She was married on 30 June 1967 to Robert Frances Weich, born 5 May 1945.
 
aa. Chris Robert Weich was born 10 October 1968.

bb. Scott Michael Weich was born 26 August 1970.

c. Julie Ann Miller was born 1 March 1951.  She was married on 11 Aug 1973 to Robert Lyn Petersen, born 13 March 1951.
 
5. Edna Alma Miller was born 24 September 1917 and died 5 December 1981. She was married on 30 September 1945 to Thomas Blair Chapman, born18 January 1913.
 
a. Thomas Miller Chapman was born 2 June 1946.  He was married on 30 August 1968 to Terry Destafano, born 28 November 1949.  He remarried on 21 June 1975 to Christine Clau, born 22 March 1953.  
			
aa. James Reed Chapman was born 15 July 1969.

bb. John Arthur Chapman was born 29 October 1971.

b. James Lee Chapman was born 8 November 1950.  He was married on 7 May 1980 to Kathleen Crane, born 10 Sept 1955.
 
aa. Cassaundra Marie Chapman was born 16 July 1973.

6. Minnie Amanda Marie Miller was born 2 November 1919 and died 15 August 1964.  She was married on 20 October 1945 to Reid Louis Houghtaling, born 4 April 1922. 

a. Constance Reed Houghtaling was born 12 October 1946.  She was married on 7 April 1967 to Carson Calvan Chism, born 31 Dec 1944.
 
aa. Brian Carson Chism was born 25 March 1973.

b. Kathhleen Ann Houghtaling was born 12 October 1946.  She was married on 29 June 1968 to Jerry Austin Loomis, born 10 Dec 1943.
 
aa. Wayne Austin Loomis was born 6 April 1972.

bb. Ann Marie Loomis was born 23 March 1974.

c. Jane Marie Houghtaling was born 14 July 1957.  

D. Edwin Friedrich August Bogenhagen was born 18 June 1881, and died 13 Feb 1960. He was married on 14 July 1907 to Anna Charlotte Marie Kiehn, born 25 June 1885, died 28 April 1928.

1. Ester Augusta Catherine Bogenhagen was born on 4 May 1908 in S.D. She was married on 20 May 1940 to Elmore William Henry Ziemann, born 9 November 1904.

a. Lyle Elmore Ziemann was born 30 April 1941, Fairmont, Minnesota. He was married on 4 November 1972 to Carol Lynn Meyer, born 30 April 1944.

aa. Michael David Ziemann was born on 30 May 1976 Missouri.

bb. Matthew Jeffrey Ziemann was born on 20 June 1978.

b. Carol Ann Ziemann was born on 17 April 1943 in Minnesota.  She was married on 16 May 1964 to Melvin Martin Edgar Schultze, born3 March 1937.  Children were born in Minnesota.

aa. Todd Charles Schultze was born 12 May 1966.

bb. Mark Layne Schultze was born 30 December 1968.

cc. Kyle Nathan Schultze was born 6 April 1971.

c. Theodore Edwin Ziemann was born 6 May 1946 in Minnesota.  He was married on 11 May 1968 to Betty Lee Reed, born 19 Aug 1945. Their children were born in Iowa.

aa. Cynthia Ann Ziemann was born 5 March 1973.

bb. Timothy Aaron Ziemann was born 24 Dec 1975.

cc. Kristen Lee Ziemann was born 28 July 1977.

2. Elsie Bertha Marie Bogenhagen was born 28 April 1910.

3. Adellia Minnie Lizzie Bogenhagen was born 21 February 1912.  She died 19 December 1994.

4. Dorothy Mathilda Helena Bogenhagen was born 22 December 1913.  She died 10 Feb 1915, buried in St. John's Cemetery south of White Lake SD.

5. Arnold Frederick William Bogenhagen was born on 5 August 1915.  He was married on 12 November 1939 to Hazel Pauline Suter, born 31 July 1911 in Washington. 
		
a. Dwaine Marvin Bogenhagen was born 22 August 1940 in Minnesota. He was married on 23 September 1962 to Roberta Ann Mathiason, born 25 November 1943 in Minnesota. 

aa. Bryon Dwaine Bogenhagen was born 5 August 1963 in Minn.

bb. Michael Arnold Bogenhagen was born 27 October 1964 in Mn.

cc. Julie Marie Bogenhagen was born 7 Mar 1975 in SD

b. Katherine Elaine Bogenhagen was born 27 Oct 1943 in Minnesota. She was married on 21 August 1965 to David Dean Ostrem, born19 September 1942 in Minnesota.  (She compiled much of the Bogenhagen data in this volume.)

aa. Kellie Jo Ostrem was born 20 Jan 1971.

bb. Heidi Lynn Ostrem was born 2 January 1973.

6. Carl Bogenhagen was born 28 January 1918 and died the same day.

7. Gustave Arthur Bogenhagen was born 19 Feb 1919 in S.Dak.  He died 5 March 1979.  He had cerebral palsy.  He was buried at St. John's Cemetary, White Lake.

8. Hermann Fredrick Bogenhagen was born 1 June 1921.  He died 16 June 1921.

9. Clara Frieda Bogenhagen was born 1 June 1921. She died 21 June 1921.

10. Hilda Alma Bogenhagen was born 7 November 1922.  She died 22 Oct 1925.

11. Elmer Edwin Frederick Bogenhagen was born 16 December 1925.  He was married on 27 May 1962 to Ida Allaine Fehn, born 24 September 1935.  Their children were born in South Dakota.

aa. Ann Marie Bogenhagen was born 24 March 1963.  She was married on 15 August 1981 to Rodney L Feltman.

bb. Douglas Wayne Bogenhagen was born 24 January 1964.

cc. Steve Edward Bogenhagen was born 27 December 1965.

dd. Elaine Alice Bogenhagen was born 16 July 1969.

ee. Mary Jane Bogenhagen was born 1 September 1972. 	

12. Raymond Arthur Bogenhagen was born 13 April 1928.  He was married on13 June 1954 to Wilma Gerlach, born 16 Nov 1931.

aa. Norma Kay Bogenhagen was born 7 April 1955 in South Dakota.  She was married 28 June 1980 to Richard Eugene Indalls, born 25 Dec 1937.
 
bb. Nancy Ann Bogenhagen was born 2 August 1957.

cc. Marcia Fay Bogenhagen was born 8 June 1959.  She was married on 30 May 1980 to Scott Jones Hanscom, born 1 September 1959.
 
dd. Betty Lee Bogenhagen was born 3 May 1964.

ee. Sue Lynn Bogenhagen was born on 21 June 1966.

E. Alma Bogenhagen was born 26 Septemper 1883. She died on 21 December 1965. She married, on 24 August 1905 Fred Bradwisch, born 16 Mar 1873, died 27 May 1937, suicide.  (Her mother was strongly opposed to the marriage.)    (Ester Minnie Frieda Bradwisch was his daughter by a previous marriage.  Her daughter, Louise Mosemann, married Lawrence Fredrick Bogenhagen.)  

1. Henry  Fred Bradwisch was born 12 October 1907,  He died 15 March 1977. He was married on 2 April 1934 to Florence Caroline Doering, born 4 Aug 1908.
 
a. LeRoy Louis Bradwisch was born 8 Nov 1935.  He was married 12 Aug 1958 to Janice Faye Olson, divorced then married Sharon Shingleman, born 1 Dec 1943.

b. Larry Lee Bradwisch was born 23 Jan 1939.  He was amrried on 20 Nov 1959 to Elizabeth Ann Baker, born 12 May 1942.
 
aa. Debbie Ann Bradwisch was born 13 June 1959.  She was married on 4 March 1978 to David Varlotto.
 
bb. Janet Lee Bradwisch was born 4 October 1960.  She was married on 24 March 1979 to James Alfred Knigge, born 10 June 1956.
 
aaa. Levi Lames Knigge was born 10 Oct 1979, died 24 November 1979.
 
cc. Brenda Lee Bradwisch was born 10 November 1962.

dd. Linda Kaye Bradwisch was born 24 Mar 1967.

c. Shirley Ann Bradwisch was born 6 August 1942.  She was married to Ronald H. Rodden in 1961.  They were divorced, and on 22 Feb 1964 she married Curvin Wendell Curtis.
 
aa. Randy Rodden was born 26 July 1961. 

bb. Rhonda Renee  Curtis was born 19 Nov 1965.

cc. Kelly Lynn Curtis was born 18 Dec 1966.

d. Robert William Bradwisch was born 3 July 1945.  He was married on 26 November 1965 to JudyKay Wether, born 18 Nov 1946.
 
aa. Tammy Kay Bradwisch was born 31 May 1966.

bb. Angie Bradwisch was born 25 July 1975.

e. Kevin Dean Bradwisch was born 30 December 1952.  He was married on 14 Feb 1980 to Rose.

f. Vicki Kay Bradwisch was born 16 March 1955.  She was married on 30 June 1972 to Dale Gerlack, born 8 August 1947.
 
aa. Amy Ellen Gerlach was born 25 August 1974.

bb. Dan Dale Gerlach was born 21 September 1976.

2. Walter Elmer Bradwisch was born 24 May 1909 and died 3 July 1923.

3. Arthur Theodore Bradwisch was born 25 October 1911.  He died on 12 March 1995. He was married on 5 September 1934 to Elnora Bannick, born 4 February 1915.

a. Vivian Elinore Bradwisch was born 26 August 1935.  She was married 11 August 1958 to Howard Dean Jacobs, born 10 Oct 1933.

aa. Curtis Lee Jacobs was born 20 Feb 1961.

bb. Dawn Marie Jacobs was born 22 September 1962.

b. Yvonne Marie Bradwisch was born 13 Jan 1937.  She was married on 7 June 1958 to Marlen Luverne Weeldreyer.
 
aa. James Marlen Weeldreyer was born 30 June 1959.

bb. Lynn Marie Weeldreyer was born 8 Nov 1960.

cc. Jeffrey Brian Weeldreyer was born 8 October 1964.

c. William Arthur Bradwisch was born 30 May 1942.  He was married on 5 June 1965 to Joyce Faye Peters, born 6 Oct 1944.

aa. Nancy Kaye Bradwisch was born 13 May 1966.

bb. Quinten Arthur Bradwisch was born 1 Dec 1968.

cc. Kerry Jo Bradwisch was born 26 June 1971.

d. Donald Edward Bradwisch was born 10 June 1944.  He was married on 24 April 1965 to LeAnne Lucille Reinisch, born 11 May 1945.
 
aa. Michelle Raye Bradwisch was born 6 Feb 1966.

bb. Cynthia Lea Bradwisch was born 20 April 1967.

cc. Todd Michael Bradwisch was born 3 Feb 1972.

dd. Troy Allen Bradwisch was born 20 Feb 1973.

4. Theodore William Bradwisch was born 19 June 1915 and died on 22 Oct 1958. He was married on 18 March 1940 to Elizabeth Ann Howard, born 18 March 1923.

a. Ruby Ann Bradwisch was born 3 July 1942.  She was married on 17 August 1962 to Jerald Dean Berndt. She remarried Nelson B. Carter on 21 June 1970.  She remarried still another time 23 May 1979 to Gary Wayne Kruse, born 11 August 1951.  

aa. John Lawrence Berndt was born 3 August 1962.

bb. Nelson B. Carter III was born 1 July 1971.

cc. Cassandra A Carter was born 23 September 1972.

dd. Jim Wayne Carter was born 20 June 1977.

b. Ruth Ann Bradwisch was born 16 Nov 1944.  She was married on 8 Jan 1965 to William Paul Goranson, born 16 Dec 1941.
 
aa. Theodore William Goranson was born 13 Dec 1967.

bb. Michael Allen Goranson was born 29 Jan 1969.

cc. Patricia Lynn Goranson was born 29 Dec 1971.

c. Donna Jean Bradwisch was born 16 July 1946 and died 22 Mar 1968.

d. Delores June Bradwisch was born 25 Oct 1947.  She was married on 20 June 1970 to Terry Lee Munich, born 20 July 1947.
 
a. Travis Lynn Munich was born 1 Dec 1971.

b. Trevor Lee Munich was born 30 Jan 1975.

c. Heath Terry Munich was born 28 November 1977.

5. Ida A. Bradwisch was born 25 Sept 1917.

6. Betha Evelyn Bradwisch was born 7 Sept 1919.  She was married on 11 July 1942 to Laurenc V. Mueller, born 30 Nov 1917.

a. Jimmy Mueller was born 13 Nov 1943.  He was married on 21 August 1970 to Dianne Patricia Vaerewyek, born 7 Jan 1946.
 
aa. Allen Mueller was born 11 Sept 1971.
 
7. Alma Florence Bradwisch was born 29 July 1923.  She was married on 23 June 1953 to Cris J. Glass, born 4 Feb 1919.
 
a. Sheila Marie Glass was born 14 Nov 1954.  She was married in 1976 to Robert  Thomas.
 
8. Lillian Anna Bradwisch was born 26 Jan 1925.  She was married on 3 Feb 1960 to Herb Davis.  They divorced.
 
F. Arthur Herman Bogenhagen was born 31 January 1886 and died 1 June 1926 from a dynamite explosion.  He was married to Anna Marie Ketelhut born 10 April 1890, died 19 February 1956.  (See Ketelhut section for her family.)

1. Viola Augusta Emma Bogenhagen was born 5 October 1914.  She died 18 October 1962.  She was married 11 June 1944 to Paul Ernest Ehrlich, born 30 May 1904, died 27 Dec 1977.

a. Deanna Lee Ehrlich was born 19 June 1945.  She was married on 23 January 1965 to Richard Earl Dowding, born 13 Nov 1936.

aa. Richard Earl Dowding Jr was born 31 Jan 1966. He was married to Kimberly Jo Liekhus.

aaa. Joshua Dowding was born 31 Dec 1989.

bbb. Sarah Jo Dowding was born 9 June 1992. 

b. Roy Dwayne Ehrlich was born 22 October 1946.  He was married 23 August 1971 to Linda Dianne Hans, born 24 Sept 1944.

aa. Matthew Paul Ehrlich was born 8 August 1971.

aaa. Alicia Elaine Ehrlich was born 16 July 1996.

bb. James Andrew Ehrlich was born 23 Feb 1975.

cc. Eric Daniel Ehrlich was born 30 July 1976.

dd. Philip Jon Ehrlich was bonr 27 Sept 1977.

2. Stella Clara Bertha Bogenhagen was born 16 July 1916. She died on 6 July 2002.  She was married on 27 December 1938 to William Pavlis, born 15 August 1912, he died 4 Jan 1984.

a. Robert Roy Pavlis was born 10 April 1941.

b. Roger Dean Pavlis was born 14 June 1946.  He was married on 9 June1967 to Karen Marie Knutsen, born 20 June 1946.  Both of their children were graduates of St. Olaf College, and were married there.

aa. Chad Loren Pavlis was born 12 August 1969.  He was married on 9 June 1991 to Amy Marie Peterson.

bb. Jeremy Mark Pavlis was born 25 Sept 1972.  He was married on 10 June 1995 to Anne Elizabeth Geise.

c. Joyce Ann Pavlis was born 18 January 1949.  She was married on 13 July 1975 to Everett Idan Tollerud, born 9 Feb 1949.

aa. Heather Joy Tollerud was born 2 March 1981.

bb. Erik Tollerud was born 13 December 1983.  

d. Gary Lee Pavlis was born 28 July 1953.  He was married on 22 Dec 1974 to Mary Lynn Stephenson, born 17 Dec 1952.
 
aa. William Lee Pavlis was born 8 August 1979.

bb. Ann Marie Pavlis was born 20 May 1982.

cc. Katherine Jean Pavlis was born 4 August 1983.

e. Terry Lynn Pavlis was born 28 July 1953.  He was married 8 Nov 1980 to Laura Serpa, born 21 July 1947.

3. Augusta Bogenhagen was born 20 Nov 1917. She died the same day.

4. Louis John Bogenhagen was born 13 September 1919, and died 8 Sept 1927.

5. Grace Minnie Clara Bogenhagen was born 28 September 1921.  She was married on 6 June 1943 to Arnold Lawrence Suelflow, born 16 July 1913.

a. Dean Alan Suelflow was born 26 May 1953.  He was married on 7 Nov 1981 to Susan Elizabeth Niehus, born 17 Nov 1956.

aa. Lindsay Ann Suelflow was born 22 April 1983.

bb. Reid Daniel Suelflow was born 17 Aug 1984.

cc. Kelsey Suelflow was born in September 1989.

dd. Melany Suelflow was born 1 June 1992.

b. Wayne Arden Suelflow was born 25 August 1956.  He was married on 31 August 1979 to Sharon Marie Koch, born 19 September 1958.

aa. Abigail Marie Suelflow was born 2 September 1980.

bb. Lucas Wayne Suelflow was born 25 July 1983.

6. Lawrence Frederick Bogenhagen was born 26 April 1924.  He died 7 Feb1990. He was married on 9 June 1953 to Louise Emma Mosemann, born 22 October 1930.

a. Janice Marie Bogenhagen was born 4 June 1954.  She was married on11 October 1975 to James Richard Schuman,  born 19 April 1955.

aa. Jason Lawrence Schuman was born 16 September 1977.

bb. Sara Ester Schuman was born 24 January 1979.

cc. Samuel James Schuman was born 17 July 1980. 

dd. Andrew John Schuman was born 19 September 1982.

ee. Jamie Marie Schuman was born 1 June 1984. 

b. Linda Rae Bogenhagen was born 10 Nov 1955.  She was married on 4 February 1978 to Roger John Munk, born 17 Sept 1949.

aa. John Lawrence Munk was born 9 August 1980.

bb. Raymond Karl Munk was born 11 October 1981.

c. Darla Elaine Bogenhagen was born 30 December 1956. She was married on 21 August 1982 to Kenneth Edwards.  They later divorced.

aa. Amber Leigh Edwards was born 2 October 1984.

d. David Edwin Bogenhagen was born 30 December 1956.  He was married on 30 September 1978 to Nancy Ellen Schochenmaier, born 11 May 1957.

aa. Kathryn Ellen Bogenhagen was born on 26 March 1985.

bb. Laura Marie Bogenhagen was born 9 April 1986.

cc. Benjamin Bogenhagen was born 20 November 1987.

dd. Brian Joseph Bogenhagen was born 2 Dec 1990.

G. Frederick Bogenhagen was born 3 May 1888, died 21 Feb 1976.  He was married on 14 December 1922 to Bertha Steffen, born 4 November 1902, died 18 Dec 1976.

1. Carl Bogenhagen was born 16 December 1923.  He was married on 15 May 1952 to Rosella Weires, born 19 May 1925.

a. Donna Bogenhagen was born 20 Oct 1952.  She was married on 1 May 1976 to Paul Viereck, born 12 May 1953.
 
b. Donald Bogenhagen was born 20 Oct 1952.  He was married on 2 June 1979 to Kathleen Lucas, born 24 June 1960.
 
c. Carol Jean Bogenhagen was born 26 Dec 1953.  She was married on 2 July 1977 to Michael Korzan, born 3 Aug 1951.
 
d. Doris Bogenhagen was born 4 May 1955.  She was married on 31 May 1974 to Thomas Furmann, born 8 July 1953.  Separated.
 
e. Julie Bogenhagen was born 8 April 1960.  She was married 26 August 1978 to Britt Bruner, born 11 Nov 1952.
 
f. Arlene Bogenhagen was born 12 April 1963.

2. Robert Bogenhagen was born 18 July 1926.  He was married on 15 April 1961 to Margaret Steichen, born 19 June 1936.  They divorced.		
 
a. Janet Bogenhagen was born 3 November 1961.

3. LaVerne Bogenhagen was born 30 April 1928.  She was married on 14 Dec 1948 to Herbert Steffen, born 18 November 1921.
 
a. Gloria Steffen was born 14 March 1950.  She was married on 24 Oct 1970 to Dean Collins, born 28 Nov 1946.
 
aa. Christopher Collins was born 10 Sept 1975.

bb. Amber Collins was born 18 Feb 1977.

b. Alice Steffen was born 12 May 1951.  She was married on 23 Dec 1972 to Mike Salonen, born 13 April 1951.
 
aa. Heidi Salonen was born 13 July 1973.

c. Terry Steffen was born 25 August 1954.

d. Dawn Steffen was born 3 November 1956.  She was married on 2 Sept 1978 to Wade Henderson, born 27 May 1957.
 
e. Myron Steffen was born 5 December 1959.
 
4. Eleanor Bogenhagen was born 27 Feb 1930.  She was married on 20 August 1949 to Alwin Peters, born 24 November 1926.  
 
a. Vicki Peters was born 13 Feb 1950.  She was married 6 Feb 1971 to Dalayne Persson, born 25 Nov 1947.
 
aa. Karin Persson was born 19 August 1971.

bb. Jon Persson was born 3 Feb 1976.

b. Gary Peters was born 1 April 1951.

c. Dennis Peters was born 8 May 1953.

d. Neil Peters was born 29 Jan 1954.

e. Cherie Peters was born 23 Feb 1956.  She was married 25 August 1979 to Dean Hopper, born 24 Jan 1954.
 
f. Brian Peters was born 19 Jan 1959.

g. Rhonda Peters was born 3 March 1960.

h. Carla Peters was born 7 Oct 1962.

i. Renee Peters was born 19 Nov 1963.

j. Craig Peters was born 22 May 1968.

5. Ila Bogenhagen was born 7 March 19324.  She was married on 20 April 1974 to Edwin Christensen, born 31 May 1924.
 
6. Arthur Bogenhagen was born 8 Oct 1936.

7. Mary Ann Bogenhagen was born 13 January 1941.  She was married on 24 Aug 1962 to Roger Scheurenbrand, born 29 June 1940.
 
a. David Scheurenbrand was born 6 Feb 1964.

b. Jim Scheurenbrand was born 14 July 1965.

c. Steve Scheurenbrand was born 24 June 1968.

H. Louis Casper Bogenhagen was born 25 April 1890.  He died in October 1918 of the flu epidemic whilst in the army during Woodrow Wilson's war to defend the British Empire.
 
I. Minnie G. Bogenhagen was born 4 July 1893 and died on 3 September 1973.  She was married on 10 April 1912.  She married Charles Markhardt, born 1 March 1886, died 8 September 1967.
 
1. Clara Markardt was born 28 Feb 1913.  She died 6 November 1975.

2. Florence Markardt was born 5 Jan 1915.  

3. Edna Markardt was born 23 December 1916, she died 14 Jan 1917.

4. Gladys Markardt was born 9 Oct 1918.  She was married on 8 May 1948 to Watler Rober, born 30 Jan 1912.  
 
a. Charlene Rober was born 23 Nov 1952.

5. Carl Markardt was born 5 November 1920.  He died 29 June1959.
 
6. Alfred Markardt was born 23 September 1923.

7. Earl Markardt was born 22 August 1925.

8. Lorraine Markardt was born 10 October 1928.  She was married on 17 Jan 1964 to Oliver Hanten, born 27 Oct 1924.
 
a. Lisa Hanten was born 3 Sept 1965. 

b. Mark Hanten was born 31 Jan 1967.

c. Lee Hanten was born 4 Sept 1970.

d. Jan Hanten was born 25 August 1972.

9. Eugene Markardt was born 29 Nov 1930.  He was married on 26 Nov 1977 to Carol Ann Krumvieda, born 18 Sept 1940.
 
a. Tanelle Markardt was born 30 Sept 1978.

10. Ruth Markardt was born 29 Jan 1933.  She was married on 23 Sept 1955 to Don Guindon, born 8 May 1927.
 
a. Marlin Guindon was born 14 Jne 1956.

b. Curtis Guindon was born 24 Nov 1957.  He was married on 2 June 1979 to Kathy Vlasman, born 31 August 1960.
 
c. Russel Guindon was born 14 Dec 1962.

d. Karla Guindon was born 25 July 1967.

e. Cory Guindon was born 12 Dec 1969.

11. Janet Markardt was born in Septembr of 1936 and died in July of 1938.

J. Bertha Helena Bogenhagen was born 1 March 1896.  She died 24 July 1961 of cancer. She was married on 16 March 1921 to Alfred Rossow, born 3 May 1895.
 
1. Irene Rossow was born 3 March 1922.  She was married on 26 June 1943 to Henry B. Bickell, born 17 Oct 1918.
 
a. Mary Bickell was born 7 Oct 1946.  She was married on 2 December 1967 to Henry Peterson, born 11 November 1945.
 
aa. Paul Peterson was born 28 June 1968.

bb. Grant Peterson was born 18 June 1969.

b. Joyce Bickell was born 29 July 1948.  She was married 5 June 1967 to Alan Hoerth, born 1 March 1946.
 
aa. Jill Hoerth was born 2 Oct 1967.

bb. Jackqueline Hoerth was born 28 Dec 1973.

c. Betty Bickell was born 22 May 1953.  She was married 1 July 1978 to Don Edwards, born 14 July 1946.,
 
2. Marvin Rossow was born 6 October 1923.  He was married 23 May 1948 to Violet Mitzel, born 12 Feb 1925.
 
a. Ross Rossow was born 14 Oct 1953.  He was married 16 Sept 1971 to Brenda Weisbeck, born 23 March 1955.
 
aa. Tracy Marie Rossow was born 25 Feb 1972.
 
bb. Sheri Dawn Rossow was born 5 June 1974.

cc. Jesse Jon Rossow was born 2 June 1981.

b. Troy Rossow was born 9 Oct 1963.

3. Elva Rossow as born 3 July 1926.  She was married on 11 Sept 1946 to Herbert Aman, born 25 Nov 1917.
 
a. Deanna Aman was born 24 Feb 1948.  She was married on 21 Dec 1965 to Charles Mauck, born 21 Jun 1947.  
 
aa. Melissa Mauch was born 14 June 1967.

bb. Jessica Mauch was born 14 Oct 1971.

cc. Brandon Charles Mauch was born 18 Oct 1980.

b. Patsy Aman was born 9 June 1952.  She was married 26 June 1976 to Emery Visto, born 21 Jan 1951.
 
aa. Shane Visto was born 3 May 1978.

bb. Erica Visto was born 26 June 1980.

cc. Chad Emery Visto was bonr 31 Oct 1981.

c. Sonya Aman was born 26 Nov 1956.  She was married on 20 May 1978 to Tim Huber, born 27 Nov 1955.
 
aa. Heidi Dee Huber was born 31 July 1980.

4. Alice Rossow was born 24 Oct 1928.  She was married on 28 October 1951 to Eugene Young, born 26 May 1926.
		 
a. Nancy Young was born 21 Feb 1957.

b. Harlan Young was born 23 Jan 1959.

c. Donald Young was born 17 July 1960.

III.Wilhelm Bogenhagen was born in the late 1850's in Germany.  He was once Burgermeister von Benz.  His wife's name was Emilie.  Wilhelm died in 1917 of Cancer.  Emilie died about the same time.

A. Mathilde Bogenhagen was born 6 Nov 1877.  She died in May 1945 whilst fleeing Benz as the Russians approached in WWII.
 
B. Richard Bogenhagen was born 4 October 1888.  He died on 8 Nov 1916 of cancer.  He married Elizabeth Wepner, born 18 Dec 1887, died 19 April 1971.  
 
1. Gunther was born 3 May 1910.  He died on 6 March 1942 in WWII.

2. Christa Bogenhagen was born 28 Dec 1915.  She was married on 24 Nov 1938 in Benz to Werner Feldt.  He was born 30 Jan 1910. He died 19 Sept 1941 in war. She was remarried on 22 Sept 1967 to Herbert Kutscher who died in 1994. 

a. Udo Feldt was born 12 May 1940.  He was married to Gisela.

aa. Silke Feldt was born 4 Oct 1969.

bb. Petra Feldt was born 4 October 1969.
	
\vskip 4mm
The End of the Bogenhagen family


\pagebreak

{\Huge \noindent Jasch Family}
\vskip 5mm
	The Jasch family is less well known than most of the other ancestors. The Jasch family came to America from Germany and landed at Ellis Island.  They moved to Mississippi, and then to Chicago.  Karl and Hanna Jasch are both buried in Chicago.  

I.  Karl Jasch was born on 2 July 1823 and died on 26 June 1904.  He was married to Hanna 
Florentine Heier, born 18 October 1831, died 27 October 1906.
 
A. Augusta Theresa Jasch was born 21 November 1856.  She died on 13 September 1939. She was married on 26 April 1873 to Friedrick W. Bogenhagen, born 6 Jan 1850, died on the twenty sixth of	 October 1916.  (See The Bogenhagen section for these.)
 
B. Bertha Jasch married Louis Peick.  He was a policeman in Chicago for many years. The two of them were so large that they had to have a special bed.  
 
1. Louis Peick Jr.

2. Gertie Peick married Walter Haug.

3. Liz Peick married a man with last name Peterson. 

C. August Jasch married Anna.

1. Walter Jasch never married.   

2. Herbert Jasch



\vskip 4mm
End of Jash family

\pagebreak

{\Huge \noindent The Ketelhut Family}
\vskip 5mm

	Daniel Ketelhut and his wife, Charlotte Wiedenhoeft,  spent their entire lives in Germany. Both were apparently born in the 1820's.  They had seven sons and one daughter.   The names and lives of the daughter and two sons are unknown.  The Ketelhut outline here gives the children of Daniel Ketelhut in capital Roman numbers, grandchildren in upper case Roman letters, great grandchildren in Arabic numbers, great great grandchildren in lower case Roman letters, and great great great grandchildren in double lower case Roman letters.

I. Gustav A. Ketelhut was born in 1851 in Germany, he died on 19 January 1928 in Mitchell South Dakota.  He married Johannah K. Goetsch.  (It is not known if she were related to the Goetsch who married Amelia Sharping.)  Both are buried in Graceland Cemetery, Mitchell, South Dakota.  They had one adopted daughter.

II. Johann Karl Friedrich Ketelhut was born 24 December 1853 in Trap-fonder-rega, Germany.  He died on 2-November 1936 in South Dakota.  He married Augusta Marie Wilhemine Sharping who was born on 25 September 1862 in Lebetzow, Germany.  She died in 1943.  They are buried in Ola, South Dakota.

A. Emma Marie Ketelhut was born on 7 September 1885 in Dodge County Wisconsin.	She died 12 May 1972.  She was married on 26 February 1908 to Otto C. Steffen (born 7 December 1878, died 8 November 1970).
 
1.  Alvina Steffen was born 5 August 1909.  She was married on 4 September 1948 to George Stahr (Born 12 May 1900, died 4 August 1986).
 
2. Raymond Steffen, born 27 February 1911, died 15 March 1911.

3. Leona C. Steffen was born 15 January 1912, died 19 August 1985;  married 21 February 1939 to John H. Sleuter (born 25 February 1912, died 21 Dec 1962).
 
4. Wilmer Emil Steffen was born 25 June 1914, married on 10 June 1952 to Suzy B. McCormick (born 26 October 1914, died 19 November 1966.  He married Marion Lippert Aarhus (born 18 Nov 1922) on 24 March 1969.
  
a. Dale Allen Steffen was born 6 January 1954, and was married on 20 December 1974 to Patricia Therry (born 6 September 1956.)
 
aa. Patrick Dale Steffen was born 14 April 1978.

5. Clara Steffen was born 27 June 1916, died 30 July 1916.

6. Florence M. Steffen was born 9 December 1917.  She was married to Weston Spenser Jakeman (born 19 July 1913)  on 23 August 1959.  She  had a twin who was stillborn.

7. Leonard Carl Steffen was born 11 January 1920 and was married on 15 Aug 1964 to Renalda Anne Gennrich (born 16 March 1941).

8. Lester Arthur Steffen was born 18 March 1922, and married on 11 February 1956 to Yvonne Elizabeth Walz (born 8 April 1935).

a. Richard Allen Steffan was born 8 Feb 1957 and died 21 Feb 1957.

b. Ronald Wayne Steffen was born 28 Jan 1958.

c. Barbara Lynn Steffen was born 26 October 1959.

d. Bruce Donald Steffen was born 14 November 1960.

e. Douglas Lee Steffen was born 14 August 1963.

9. Helen I. Steffen was born 15 May 1923 and married on 21 February 1948 to Gerald Allen (born 9 May 1926).

a. Randall Lynn Allen, born 29 Jan 1949, died 31 Jan 1949.

b. Deborah Kay Allen, born 5 February 1953.  Married on 25 September 1976 to  Greg Feneray.

c.  Pamala Sue Allen, born 2 September 1953, married on 7 October 1979 to Dr. Arthur M. Imoshito.

10. Agnes Steffen was born 30 December 1925 and married Mynard Grapenitine (born 10 December 1926).

11. Donna Mae Steffen was born on 6 April 1929, and married Arnold Jensen, who was born on 13 January 1927.  Wedding was held on 25 Feb 1958. 

a. Brian Jon Jensen was born 19 February 1963.

b. Timothy Scott Jensen was born 9 May 1964.

B. Martha Ketelhut was born 27 January 1887 in Wisconsin and died at age 7.

C. Arthur Albert Ketelhut was born 6 April 1988 in Lansing, Iowa.  He died on 6 December 1953.  He married Mary Ellen Weekly on 8 March 1944.

D.  Anna Marie Ketelhut was born on 10 April 1890 in South Dakota.  She died on19 February 1956.  She was married on 26 March 1913 to Arthur Herman Karl Bogenhagen, born 31 January 1886, died 1 June 1926.

1. Viola Augusta Emma Bogenhagen was born 5 October 1914.  She died 18 October 1962.  She was married 11 June 1944 to Paul Ernest Ehrlich, born 30 May 1904, died 27 Dec 1977.

a. Deanna Lee Ehrlich was born 19 June 1945.  She was married on 23 January 1965 to Richard Earl Dowding, born 13 Nov 1936.

aa. Richard Earl Dowding Jr. was born 31 Jan 1966. He was married to Kimberly Jo Liekhus.

aaa. Joshua Dowding was born 31 Dec 1989.

bbb. Sarah Jo Dowding was born 9 June 1992. 

b. Roy Dwayne Ehrlich was born 22 October 1946.  He was married 23 August 1971 to Linda Dianne Hans, born 24 Sept 1944.

aa. Matthew Paul Ehrlich was born 8 August 1971.

aaa. Alicia Elaine Ehrlich was born 16 July 1996.

bb. James Andrew Ehrlich was born 23 Feb 1975.

cc. Eric Daniel Ehrlich was born 30 July 1976.

dd. Philip Jon Ehrlich was born 27 Sept 1977.

2. Stella Clara Bertha Bogenhagen was born 16 July 1916.  She was married on 27 December 1938 to William Pavlis, born 15 August 1912, died 4 Jan 1984.

a. Robert Roy Pavlis was born 10 April 1941.

b. Roger Dean Pavlis was born 14 June 1946.  He was married on 9 June 1967 to Karen Marie Knutsen, born 20 June 1946.
 
aa. Chad Loren Pavlis was born 12 August 1969.  He was married on 9 June 1991 to Amy Marie Peterson.

bb. Jeremy Mark Pavlis was born 25 Sept 1972.  He was married on 10 June 1995 to Ann Geise.

c. Joyce Ann Pavlis was born 18 January 1949.  She was married on 13 July 1975 to Everett Idan Tollerud, born 9 Feb 1949.

aa. Heather Joy Tollerud was born 2 March 1981.

bb. Erik Tollerud was born 13 December 1983.  

d. Gary Lee Pavlis was born 28 July 1953.  He was married on 22 Dec 1974 to Mary Lynn Stephenson, born 17 Dec 1952.

aa. William Lee Pavlis was born 8 August 1979.

bb. Ann Marie Pavlis was born 20 May 1982.

cc. Katherine Jean Pavlis was born 4 August 1983.

e. Terry Lynn Pavlis was born 28 July 1953.  He was married 8 Nov 1980 to Laura Serpa, born 21 July 1947.

3. Augusta Bogenhagen was born 20 Nov 1917, died same day.

4. Louis John Bogenhagen was born 13 September 1919, and died 8 Sept 1927.

5. Grace Minnie Clara Bogenhagen was born 28 September 1921.  She was married on 6 June 1943 to Arnold Lawrence Suelflow, born 16 July 1913.

a. Dean Alan Suelflow was born 26 May 1953.  He was married on 7 Nov 1981 to Susan Elizabeth Niehus, born 17 Nov 1956.

aa. Lindsay Ann Suelflow was born 22 April 1983.

bb. Reid Daniel Suelflow was born 17 Aug 1984.

cc. Kelsey Suelflow was born in September 1989.

dd. Melany Suelflow was born 1 June 1992.

b. Wayne Arden Suelflow was born 25 August 1956.  He was married on 31 August 1979 to Sharon Marie Koch, born 19 September 1958.
 
aa. Abigail Marie Suelflow was born 2 September 1980.

bb. Lucas Wayne Suelflow was born 25 July 1983.

6. Lawrence Frederick Bogenhagen was born 26 April 1924.  He died 7 Feb 1990. He was married on 9 June 1953 to Louise Emma Mosemann, born 22 October 1930.

a. Janice Marie Bogenhagen was born 4 June 1954.  She was married on 11 October 1975 to James Richard Schuman,  born 19 April 1955.

aa. Jason Lawrence Schuman was born 16 September 1977.

bb. Sara Ester Schuman was born 24 January 1979.

cc. Samuel James Schuman was born 17 July 1980.

dd. Andrew John Schuman was born 19 September 1982.

ee. Jamie Marie Schuman was born 1 June 1984. 

b. Linda Rae Bogenhagen was born 10 Nov 1955.  She was married on 4 February 1978 to Roger John Munk, born 17 Sept 1949.

aa. John Lawrence Munk was born 9 August 1980.

bb. Raymond Karl Munk was born 11 October 1981.

c. Darla Elaine Bogenhagen was born 30 December 1956.  She was married on 21 August 1982 to Kenneth Edwards.  They divorced.

aa. Amber Leigh Edwards was born 2 October 1984.

d. David Edwin Bogenhagen was born 30 December 1956.  He was married on 30 September 1978 to Nancy Ellen Schochenmaier, born 11 May 1957.

aa. Kathryn Ellen Bogenhagen was born on 26 March 1985.

bb. Laura Marie Bogenhagen was born 9 April 1986.

cc. Benjamin Bogenhagen was born 20 November 1987.

dd. Brian Joseph Bogenhagen was born 2 Dec 1990.
				
E. Olga Martha Ketelhut was born 4 April 1892 in South Dakota.  She died on 5 July 1965.   On 14 July 1914 she married Edward Priebe, born 18 Feb 1885, died 9 Nov 1967. She was such a cheerful lady that her good humour are remembered by everyone for years after her death.

1. Pearl Winifred Priebe was born 29 July 1918.  She was married on 28 August to Warren Lorraine Parriot, born 9 May 1920, died 29 December 1965.

a. Dennis Lynn Parriot was born on 31 October 1949.   To Constance Luann Goodwin who died 21 December  1972.

b. Lorelei  Naomi Parriot was born 19 November 1951.  She was married on 25 April 1983 to Robert Nordorf.

2. Lola Priebe was born 23 August 1920.  She was married on 25 Sept 1948 to Theron Hudson Wilson, born 10 December 1916.

a. Kurt Edward Wilson was born 14 February 1950.  He was married on 16 September 1971 to Linda McMullin, born 30 May 1950.

aa. Kristine Lynn Wilson was born 22 August 1973.

bb. Bryan Edward Wilson was born 1 November 1974.

cc. Jennifer Leigh Wilson was born 1 March 1977.

dd. Rebecca Emily Wlson was born 4 May 1979.

ee.  Brandon Jeffrey Wilson was born 20 July 1981.

ff.  Kathereine Marie Wilson was born 2 August 1983.  

b. Craig Alfred Wilson was born 26 January 1951.  He was married on 31 August 1972 to Sandra Loder, born 22 March 1951.

aa.  Cami Ann Wilson was born 21 October 1974.

bb. Samuel Spencer Wilson was born 14 March 1976.

cc. James Wade Wilson was born 21 January 1981.

dd. Amy Lee Wilson was born 21 May 1984.

ee. Clayton Kenneth Wilson was born 30 March 1986.

c. Scott Theron Wilson was born 2 August 1953.  He was married on14 August 1973 to Elaine Rowland born 3 March 1954.

aa. Rowland Scott Wilson was born 15 July 1975.

bb. Blake Hudson Wilson was born 15 April 1977.

cc. Joy Wilson was born 13 Jan 1980 (twin).

dd. Christian Blair Wilson was born 13 Jan 1980 (twin).

ee. Richard Mark Wilson was born 23 April 1985.

ff. Laura Elizabeth Wilson was born 27 August 1988.

d. Kevin P. Wilson was born 9 May 1956.  He was married on 2 March1988 to Kathy Ford.

aa. Tyler Jan Wilson was born 12 February 1990.

e. Suzanne Wilson was born 12 July 1957, married on 29 June 1979 to Michael Conrad Lantz, born 1 Sept 1956.

aa. Colin Michael Lantz was born 17 Feb 1981.

bb. Brady Jan Lantz was born 19 October 1982.

cc. Casey Conrad Lantz as born 14 November 1985.

dd. Kyle Edward Lantz was born 30 April 1988.

f. Jay Brian Wilson was born 4 August 1958, died 12 November 1961, he was run over by  a car.

3.  Kenneth Priebe was born 24 January 1930.  He was married on 7 May 1983 to Dolly Parker, born 1 April 1931.  He departed from this life on 13 Jan 1997.

F. Emil Johannes Ketelhut was born on 9 April 1894 in S.D.  He died on 17 Sept 1978. He was married on 6 June 1923 to Frieda Emma Drafahl, born 24 Feb 1905, died 30 Jan 1971.

1. Ivan Donald Ketelhut was born 9 Feb 1925.

2. Betty June Ketelhut was born 10 June 1927.  She was married on 22 June 1947 to Joe Callen, born 11 October 1922.

a. Wayne Leon Callen was born 16 October 1948.

b. Craig Eugene Callen was born 26 Jan 1955.

3. Merle Eugene Ketelhut was born 16 March 1930. He was married on 17 Nov 1957 to Nila Faye Korzan, born 6 August 1934.

a. Brian Merle Ketelhut was born 16 December 1961.  He was married on 15 June 1985 to Tamara Creager, born 26 Sept 1963.

aa. Kayla Marie Ketelhut was born 31 May 1987.

b. Mark Eugene Ketelhut was born 1 September 1963.

c. James Lee Ketelhut was born 9 June 1967.

4. Genevieve Louise Ketelhut was born 20 Feb 1932.  She was married on 2 Jan 1955 to Ralph W. Yocum, born 13 June.

a. Jeanette Yocum was born 30 May 1956.

b. Ivan Dare Yocum was born 14 July 1958.

c. David Michael Yocum was born 8 October 1960.

d. Ann Louise Yocum was born 6 July 1963.

G. Gustav William Ketelhut was born 26 August 1896 in South Daktoa.  He died 19 October 1972.  He was married on 7 August 1922 to Louisa Eastman, born 23 Sept 1902, died 12 August 1966. (LaVisa)

H.  Minnie Cora Ketelhut was born 4 May 1899.  She died 7 June 1990.  She was married on 14 September 1921 to Erwin Fascher.  He was born 17 March 1900, and he died 21 April 1983.

I. John William Ketelhut was born 25 July 1901 and died 28 November 1980.  He was married on 18 April 1928 to Soyfia Drafahl, born 24 August 1908.  (Frieda's sister.)

1. Donald Dewayne Ketelhut was born 3 June 1930, died 17 August 1991.  He was married on 2 August 1958 to Sally Wieshaar.  They were divorced.

a. Gregory Dewayne Ketelhut was born 2 March 1959.

b. Dori Dee Ketelhut was born 15 Jan 1961, married on 10 April 1981 to Vera Danberry.

aa. Rebecca Christine Danberry was born on 8 September 1982.

c. Tina Marie Ketelhut was born 16 April 1970.

d. Donald Ketelhut Jr. was born 22 December 1971.

2. LeRoy Marvin Ketelhut was born 29 Jan 1932.

3. Marvin Eugene Ketelhut was born 2 October 1934.  He was married on 20 June 1958 to Mary Hague, born 7 July 1932.

a. Marsha Sue Ketelhut was born 1 August 1959.  She was married on20 June 1976 to Lowell Schierkolk, born 20 November 1955.

b. Kevin Eugene Ketelhut was born 3 Feb 1965.

4. Jerome Frederick Ketelhut was born 25 June 1938.  He was married on 17 June 1972 to Betty Lengkeek, born 9 December 1947.

a. Lisa Ann Ketelhut was born 16 Feb 1974.

b. Jeffrey Jerome Ketelhut was born 13 March 1976.

J. Clara Bertha Ketelhut was born 22 February 1904.  She was married on 20 Feb 1927 to Harold Gray, born 17 September 1904, died 2 July 1983.  Clara departed from this transitory life on 19 January 1997.  

1. Ruth Gray was born 22 November 1927.  She was married on 20 April 1947 to Raymond Hloucha.  They adopted two children.

a. Marla Hloucha, born 12 May 1959, died in 1994.  Married  on 1 June 1979 to Peter Kowenhoven, born 26 May 1960.

b. Dana Hloucha, born 15 August 1961.

2. Ralph Willis Gray was born 1 May 1931.  He was married on 8 March 1959 to Nolaine Wilma Drew, born 9 December 1937.  Divorced.

a. Bret Holden Gray was born on 11 July 1960.  He was married on 15 September  1984 to Darla Kaye Davenport, born 25 Dec 1963.

aa. Holden Lee Gray was born 6 May 1990.

b. Kyle Ralph Gray was born 17 March 1963.  He was married on 11 August 1984 to Cheryl Faye Sinclair, born 6 Feb 1964.

aa. Jerod Michael Gray was born 21 May 1988.

c. Kellie Jo Gray was adopted, born 23 June 1969.

d. Nicole Lane Gray was born 28 July 1973.

III. Wilhelm Ketelhut was born on 5 July 1855 in Germany.  He died on 18 December 1927 in Stetsonville, Wisconsin.  He was married on 30 October 1882 to Wilhemine Rasch who was born on 5 September 1988 and who died 25 February 1933.   

A. Max Frank Ketelhut was born 6 September 1883 in Lebanon, Wisconsin.  He died on 7 March 1963.  He was married on 23 June 1915 to Rose Alma Daentl who was born 7 Jan 1897.  

1. Lorraine Ketelhut was born 30 June 1918.  In June 1941 she married James Cotter, born 30 July 1918.  

a. Robert  Cotter was born 7 December 1948.  His wife's name is Eileen.

aa. Lorrie Rose Cotter was born 24 July 1978.

2. Leslie Alvin Ketelhut was born 9 August 1921.  He was married on 5 Dec 1942 to Harriet Boles, born 22 October 1924.

a. Beverly Ketelhut was born 7 April 1945.  She was married on 7 Nov 1970 to James Weister, born 10 April 1944.

aa. Tommy Weister was born 12 June 1971.

bb. Wendy Weister was born 30 Nov 1972.

cc.  Michael Weister was born in May 1978.

b. Larry Lee Ketelhut was born on 14 May 1949.  He was married on 7 June 1975 to Diane Warden, born 24 June 1949.

c. Jack Marvin Ketelhut was born 23 September 1952.  He was married on 3 August 1974 to Sally Loucks, born 18 December 1951.

aa. Scott Marvin Ketelhut was born 21 October 1978.

bb. Lori  Jean Ketelhut was born Oct 1980.

d. Cheryl Ann Ketelhut was born 7 August 1959.

e. Scott Cory Ketelhut was born 3 March 1965.

3. Edwin Richard Ketelhut was born 9 March 1923.  He was married on 7 June 1947 to Catherine Multerer, born 15 January 1923.

a. Edwin John Ketelhut was born 29 February 1948.  He was married on 31 May 1972 to Randi Roberts.

aa. Edwin Ketelhut was born in 1975.

bb. Eric Ketelhut.

cc. Everett Ketelhut.

b.  Carla Ketelhut was born 19 August 1950.  She married John Stewart.

aa.  Matthew Stewart.

bb. Chad Michael Stewart.

c. Donna Ketelhut was born 9 August 1956.  She was married on 14 May 1975 to Kirk Redburn.

aa. Kirk Redborn, Jr.  was born in 1976.

bb. Christopher Robert Redburn was born 10 Feb 1979.

d. William Ketelhut was born 20 June 1958.

e. Michelle Ketelhut was born on 2 October 1960.  She was married in 1981 to Richard Anon.

f. Thomas Ketelhut was born 9 October 1962.

g. Michael Ketelhut was born 2 March 1965.

B. Johann Ketelhut was born 24 June 1885 in Lebanon, Wisconsin.  He died 11 Sept 1886.

C.  Emil Karl Ketelhut was born 7 March 1887 in Lebanon, Wi.  He died 22 April 1964.

D. Maria Ketelhut was born 8 April 1889 in Lebanon, Wi.  She died 23 March 1895.

E. Anna Ketelhut was born 8 Nov 1890 in Lebanon, died 30 Dec 1970 in Marshfield, Wi. She was married on 20 October 1912 at Stetsonville to Raymond Bert, born 13 March 1885, died 28 July 1970.  They are buried in Marshfield.

1. Ruth Berg was born 8 August 1913.  She died 24 June 1966.  She was married on 13 August 1930 to Leslie Kiehl, born 1906, died 2 June 1957.  They are buried in Marshfield.

a. Geraldine Kiehl was born 20 May 1929.  She was married on 18 August 1948 to Willard Behling, born 2 August 1919.  

aa. Linda Behling was born 24 Jan 1950.  She was married on 20 Nov 1977 to Stephen Raap who was born 21 Feb 1953.

bb. Ray Behling was born 11 June 1951.  He was married on 20 Sept 1980 to Jan Becker.

cc. Ronald Behling was born on 11 June 1951.  He was married in September 1977 to Sue Straub born 21 October 1955.

aaa. Alisa Sue Behling was born 28 Dec 1981.

dd. David Behling was born 17 May 1959.

ee. Michael Behling was born 23 Oct 1961.

ff. Daniel Behling was born 5 September 1964.

b. Bernadien Kiehl was born 4 March 1931.   She was married on 1 July 1950 to Peter Spatz, born 28 September 1928.

aa. Sally Spatz was born 26 January 1951.  She was married on 16 August 1975 to Jerrold Leschensky who was born in October 1950.He was killed in an accident on 31 October 1977. She remarried	on 16 July 1979 to Gordon Reckelberg, born 18 July 1934.

aaa. Jerrold Leschensky, Jr was born 4 July 1977.

bb. Sandy Spatz was born 5 July 1954.  She married Thomas Crum, born 18 August 1954.

aaa. Thomas Crum Jr. was born 16 August 1976.

bbb. Terry Ann Crum was born 30 August 1977.

ccc. Tonya Crum was  born 17 Oct 1979.

ddd. Timmy Crum was born 21 June 1982.

cc. Cheryl Spatz was born 11 March 1958.

dd. Carol Spatz was born 22 December 1959.

c. Willard Kiehl was born 11 October 1932.  He was married on 1 Oct 1955 to Janet Hamus, born 27 June 1937.

aa. Ricky W. Kiehl was born 7 August 1956.  He died on 30 Sept 1958 from being run over by truck.

bb. Janine Kiehl was born 4 September 1959.  She married Brian Reinhard, born 16 February 1959.

aa. Cory Lee Reinhard was born 1 July 1978.

cc. Timmy Kiehl was born 24 April 1961.

dd. Dean Kiehl was born 28 January 1964.

d. Daryl Kiel married Harriet Mueller.

e. Darvin Kiehl married Carol.

f. Darnell Kiehl was born April 1937.  She married Steven Ziegden.

g. Cindy Kiehl

F. Adelia Ketelhut was born 21 September 1896.  She died in May of 1984.  She was married on 17 April 1926 to Lawrence Liberty, born 4 May 1890, died 7 Sept 1947.

1. Pierce W. Liberty was born 11 Nov 1926.  He was married on 6 June 1953 to Adelaide Schnecker, born 11 Jan 1924.

2. Mary Ann Liberty was born 19 April 1928.  She was married on 27 Dec 1950 to Robert A. Bjornstad, born 12 July 1927.

a. Nancy Bjornstad was born 7 Feb 1951.  She was married on 1 May 1976 to Joseph Elcano, born 9 Dec 1942.

b. William Bjornstad was born 7 December 1954, he died 16 July 1970.

3. Joseph Liberty was born 19 Dec 1929, and died on 19 March 1931.

4. Dorothy Liberty was born 6 August 1932,  She was married on 8 September 1956 to J. B. Gregory, born 1 Jan 1931.

a. Thomas Gregory was born 26 June 1958.

b. Jane Gregory was born 26 Nov 1958.

c. Margaret Gregory was born 17 March 1961.

d. Mary Beth Gregory was born 12 Dec 1966.

5. Lawrence Liberty was born 14 Sept 1936.  He was married on 6 June 1959 to Katherine Morrissy, born 8 April 1928.

IV. Herman Ketelhut was born in 1858 in Germany.  He died in 1940.  He was married to Marie Haack who was born in 1859 in Germany.  She died in 1934.  Both are buried in the Lutheran Cemetery in Waterton, Wisconsin.

A. Emil  Ketelhut was born 15 October 1886.  He died on 18 February 1956.  He was married on 1 Oct 1924 to Helen Steckling, born 28 March 1884, died 19 Feb 1978. They are buried in Watertown, Wisconsin.

B. William Arthur Ketelhut was born in 1890.  He died on 12 March 1925.  He was married in 1919 to Lucille Barnes.  He is buried in Oak Hill Cemetery.  She was cremated.

1. William Thomas Ketelhut was born 29 March 1920 at Camp Jackson, SC.  He was married on 20 April 1963 to Virginia Lee Atkinson, born 24 Jan 1929.  She had three children from a previous marriage.  

a. William Earl Ketelhut was born 19 July 1964.

2. John David Ketelhut was born 23 November 1921.  He was married on 29 Oct 1949 in Winsor, Ontario, to Mae Agnes Martenette, born 3 May 1924.

a. Richard William Ketelhut was born 26 Jan 1951.  He was married on 20 September 1975 to Patricia Mereles, born 15 July 1952.

b. Kurt Matthew Ketelhut was born 11 Jan 1952.  He died 14 Sept 1974 in Fort Hood, Texas.  

c. Thomas Arthur Ketelhut was born 16 Dec 1953.  He was married on 29 April 1978 to Pamela Drouillard, born 27 Feb 1954.

d. John Joseph Ketelhut was born 25 June 1956.

V. Frank August Ketelhut was born 12 October 1864 in Streckenin, Germany.  He died on 25 March 1951 at rr\#1 Neosho, Wisconsin.  He was married on about 1864 in Germany to Ernestine Treichel, born 8 March 1863 in Germany, died in July of 1901.  She is buried in Immanuel Cemetery,  Old Lebanon, Wisconsin.  After her departure from this life, he married, on 12 October 1905, Rosalie Schneider, born 3 July 1879 in Switzerland, died 22 March 1957.  His children starting with Lillian are hers.

A. Anna A Ketelhut was born 5 February 1885 in Germany.  She died on 25 March 1962. She was married on 10 November 1907 to Walter H Schmidt, born 6 May 1885, died 17 July 1974.

1. Florence Ketelhut was adopted.  She was born 10 Dec 1913.  She was married on 8 August 1931 to Walter J. Menke, born 25 Feb 1901, died 17 July 1974.

a. Wallace Menke was born 12 Feb 1932, married on 23 Oct 1954 to Nancy Buss, born 17 June 1937.

aa. Scott Menke was born 25 Feb 1956, married on 9 June 1978 to Jane Dahl, born 16 Aug 1957.

aaa. Ryan Scott Menke was born 18 November 1983.

bbb. Jessica marie Menke was born 24 March 1986.

bb. Greg Menke was born 18 March 1957.  He was married 17 July 1982 to Eileen Plath, born 3 July 1958.

aaa. Kathleen Marie Menke was born 10 Sept 1984.

bbb. Kristi Nicole Menke was born 11 June 1987.

cc. Dena Menke was born 21 Oct 1959.

dd. Tama Menke was born 9 Sept 1961.  She was married on 28 May 1983 to Timothy Joe Ehlers, born 8 Nov 1955.

aaa. Joshua Lovel Elhers was born 13 March 1984.

bbb. Nathaniel Paul Ehlers was born 6 May 1985.

ccc. Jonathan Aaron Ehlers was born 24 July 1986.

ddd. Benjamin Ahlers was born 4 May 1988.

eee. Tabitha Ehlerw was born 7 April 1990.

fff. Micah Justin Ehlers was born 23 April 1992.

ee. Keith Menke was born 5 July 1963.

ff. Rhonda Menke was born 16 Nov 1965.

gg. Carla Menke was born 17 Jan 1969.

hh. Laura Menke was born 8 July 1970.

ii. Sara Menke was born 3 Feb 1973.

b. Marilyn Menke was born 25 Sept 1934.  She was married on 1 Sept 1956 to Norbert Neuman, born 29 July 1932.

c. Kay Ann Menke was born 25 Dec 1938.  She was married on 27 Dec 1958 to Frederick Krause who was born 3 August 1937.

aa. Todd Krause was born 20 Feb 1963.

bb. Shawn Krause was born 7 April 1966.

B. Bertha Emilie Augusta Ketelhut was born 13 Nov 1886 in Germany.  She died 15 September 1970.  She was married on 26 Nov 1908 in Neosho Wisconsin to Paul Frank Gustave Grulke, born 31 Oct 1887, died 13 June 1958.  They were buried in Oakland Cemetary, Beaver Dam, Wisconsin.

1. Leona Bertha Grulke was born 23 Nov 1909.  She died 17 Jan 1910.

2. Nora Anna Grulke was born 26 July 1914.  She was married on 15 Oct 1933 to Arnold Christian, born 14 Jan 1901, died 28 June 1996.

a. Arville Mae Christian was born 6 August 1936.  She was married on 28 June 1958 to Harold Voigt, born 18 June 1937.

aa. Kelly Scott Voigt  was born 19 Dec 1959.  She was married on 4 June 1988 to Linda Mann.

aaa. Jordan Scott Mann was born 8 April 1992.

bbb. Austin Robert Mann was born 26 August 1994.
				
bb. Vicki Lei Voight was born 7 Dec 1962.  She was married on 6 August 1983 to Timothy Paul Magnor, born 10 July 1962.

aaa. Kayla Mae Magnor was born 8 March 1989.

bbb. Andrew Timothy Magnor was born 29 Sept 1992.

b. Delmar Arnold Christian was born 7 March 1939.  He was married on 8 November 1958 to Phillis Jaeger, divorced, then he remarried on 15 May 1982, Mary Jean Klauer.

aa. Neal Christian was born 30 April 1959.  He was married on 6 October 1979 to Julie Ann Wilson, born 28 Dec 1959.

aaa. Amber Lynn Christian was born 7 Jan 1981.

bbb. Justen Neal Christian was born 16 Jan 1984.

bb. Dana Christian was born 2 August 1962, married on 2 July 1983 to George Michael Preiss.

aaa. Derick Michael Preiss was born 15 Sept 1984.

bbb. Courtney Ann Preiss was born 1 Dec 1988.

c. Anita Norma Christian was born 2 Nov 1942.  She was married on 17 Dec 1969 to Eugene Borchardt, born 9 Jan 1941. 

aa. Tracy Borchardt was born 27 May 1961,  and married on 9 May 1987 to Gay A. Dembek, born 21 Oct 1960.

aaa. Alexandra Taylor Borchardt was born 19 Feb 1994.

bb. Kimberly Borchardt was born 18 Sept 1962.  She was married on 17 Oct 1992 to Larry Schmidt, born 5 Dec 1963.

aaa. Jacob Taylor Schmidt was born 24 April 1995.

3.  Arthur Fred Charles Grulke was born 24 Nov 1916.  He was married on 15 April 1944 to Leona A. Dopperpuhl, born 5 Feb 1907, died 21 March 1985.  He was the original author of this Ketelhut family register.

a. Dale Arthur Grulke was born 22 June 1945.  He was married on 13 Oct 1973 to Marilyn Louise Bartelt, born 24 May 1949.

aa. Paul Michael Grulke was born 6 June 1975.

bb. Elizabeth Ann Grulke was born 6 July 1978.

b. Dennis Carl Grulke was born 7 July 1947.   He was married on 28 Dec 1968 to Mary Louise Hammer, born 31 Oct 1947.

aa. Tammy Lyn Grulke was born 2 Nov 1969.

bb. Jeffrey Scott Grulke was born 25 Mar 1972.

cc. Cynthia Ann Grulke was born 11 May 1975.

dd. Michele Kay Grulke was born 27 Feb 1978.

c. Daniel William Grulke was born 28 July 1949.  He was married on 22 May 1971 to Cheryl Lyn Nehl, born 19 July 1949.  They were divorced in May of 1981, but they were married again on 4 August 1989.  

aa. Brenda Jean Grulke was born 29 April 1974.

bb. Brian Daniel Grulke was born 5 July 1976.

4. Reinhard Edwin Grulke was born 29 July 1921.  He was married on 6 June 1943 to Norma A. Christian, born 15 June 1922, died 1 Nov 1988.

a. Carolyn Norma Grulke was born 28 May 1944.  She was married on 28 June 1971 to Peter Thompson, born 15 Mar 1937.

aa. Robin Kay Thompson was born 13 August 1974.

bb. Heidi Lyn Thompson was born 19 March 1977.

b. Phyllis Elaine Grulke was born 7 July 1946.  She was married on 26 May 1966 to Garold Bartel, born 18 June 1943.

aa. Rebecca Lea Bartel was born 8 Nov 1967.

bb. Ronda Lynn Bartel was born 11 March 1970.  She was married on 26 June 1993 to Troy D. Neidert.

cc. Ruth Ann Bartel was  20 March 1976.

dd. John Paul Bartel was born 14 July 1981.

ee. Rachel Marie Bartel was born 23 January 1986.

c. Frederick Reinhard Grulke was born 4 October 1948.  He was married on 5 July 1969 to Sandra Koepsell, born 12 July 1948.

aa. Matthew Grulke was born 26 Dec 1969.

bb. Michael Grulke was born 19 Dec 1970.

cc. Shawn Steven Grulke was born 12 Sept 1975.

dd. Sarah Marie Grulke was adopted from India born 1974.

ee. Melinda Jean Grulke was born 27 June adopted from Korea.

d. Steven Paul Grulke was born 19 April 1953, He was married on 12 December 1987 to Nancy Mae Lueck. born 13 Jan 1959. 

aa. Allison Maria Grulke was born 25 April 1990.

bb. Cassandra Jo Grulke was born 6 July 1992.

e. Eugene Lee Grulke was born 20 Feb 1956.  He was married on 7 Aug 1976 to Cheryl Ann Forster, born 4 Oct 1956.

aa. Jason Michael Grulke was born 15 April 1978.

bb. Timothy Eugene Grulke was born 30 Jan 1980.

cc. Jennifer Marie Grulke was born 23 Jan 1985.

f. Richard Grulke was born 25 Sept 1966.

5. Hilbert Gustav Grulke was born 1 July 1925.  He was married on 6 October 1946 to Wieda Pieper, born 26 Feb 1920.  

a. Hilbert Grulke was 12 August 1947, married on 20 April 1968 to Susan Martin, born 31 December 1946.

aa. Carrie Grulke was born 28 September 1968.

bb. Lance Grulke was born 3 March 1972.

b. Marvalene Grulke was born 11 April 1953.  She was married on 7 October 1978 to Thomas Wolter, born 24 June 1935.  

aa. Brittany Ann Wolter was born 20 August 1986.

6. Norbert Paul Grulke was born 15 June 1929, he died 19 December 1993. He was married on 29 May 1954 to Barbara Fehrman, born 26 May 1936.

a. Randall Norbert Grulke was born 21 June 1955.  He was married on 5 Nov 1977 to Lynn Reidl, born 26 August 1952. 

aa. Aaron Randall Grulke was born 6 March 1979.

bb. Brett Grulke was born 18 July 1985.

b. Dawn Denise Grulke was born 12 October 1956.  She was married on 9 October 1976 to Michael Pirkel, born 28 Sept 1956.

aa. Kelly Michelle Pirkel was born 14 Nov 1977

bb. Jaquelyn Suye Pirkel was born 14 Nov 1977.
				
cc.  Katie Elizabeth Pirkel was born 9 May 1980.

dd. Ashley Jo Pirkel was born 6 August 1984.

c. Todd Allen Grulke was born 29 Sept 1969.  He was married on 17 July 1982 to Lei Lani Dunn, born 10 Dec 1961.

aa. Elisha Media Grulke was born 21 Dec 1982.

bb. Shane Todd Grulke was born 4 May 1985.

d. Joel Anthony Grulke was born 17 Jan 1967.  He was married on 23 July 1989 to Amy Jean Eckert.

aa. Anne Elizabeth Grulke was born 24 May 1990.

bb. Nathaniel Grulke was born 26 May 1992.

C. Martha Ketelhut was born 7 July 1889 in Lebanon, Wisconsin.  She died on 14 July 1980.  She was married on 10 Nov 1907 to Fred Pfarrer, born 25 Oct 1882 in Switzerland, died 11 March 1951. 

1. Clara Rose Bertha Pfarrer was born 16 Dec 1908.  She was first married on 10 October 1925 to Theodore Hedrman Jass, born 8 July 1900, died 24 Nov 1967.  They divorced.  She married Peter Lamp born 31 July 1913, died 1 Nov 1966.  She married a third time in 1971 to Leslie Korth, born 21 August 1925, drowned  in December 1989.  

a. June Jass was born 27 June 1926 and died 18 Dec 1945.  She was married to William Gardner who died in 1946.

b. Lois Joy Jass was born 31 July 1927.  She was married on 5 June 1948 to Robert Dewitt, born 1 Jan 1927.

aa. John Alan DeWitt was born 3 Feb 1951.  He was married on 19 August 1972 to Claudia Beard, born 27 August 1953.  They were divorced, Second marriage 7 June 1980 to Lisa Ann Idmasl.

aaa. Clinton DeWitt was born 13 June 1973.

bbb. Tracie DeWitt was born 25 March 1975.

bb. Gary Robert DeWitt was born 18 February 1953.  He was married on 11 August 1979 to Mrs. Janice Whiting, born 26 Sept 1955.  

cc. Sharon Lee DeWitt was born 28 August 1959.

dd. Michael Drew DeWitt was born 7 August 1971.

ee. Diana Lynn DeWitt was born 5 Nov 1963.  

c. Theodore Jass, Jr was born and died in infancy.

d. Carol Jean Jass was born and died in infancy.

e. Kennth Roy Jass was born 6 June 1940.  He was married on 28 Dec 1965 to Kathy Homelvig, born 29 Dec 1946.

aa. Christopher Jass was born 10 July 1970.

bb Kati Jass was born 21 Nov 1974.

2. Alvin Pfarrer was born 10 Sept 1910 and died 19 March 1949.  He was married on 6 October 1936 to Gertrude Maas, born 21 Oct 1913.  

a. Merry Pfarrer was born 25 Dec 1938.   She was married on 29 Oct 1960 to James Schuyler, born 22 Oct 1938.  They divorced.  She later remarried.

aa. Cheryl Marie Schuyler was born 7 July 1961.  Died in bus accident, 17 August 1982.

bb. Susan Marie Schuyler was born 9 Nov 1965.  She was married on 10 May 1986 to Edwin Sorenson.

b. Judy L. Pfarrer was born 9 November 1942.  She was married on 28 August 1966 to Donavan Winckler, born 26 July 1938.

aa. Jaison Winckler was born 17 June 1970.

bb. Darin Eric Winckler was born 25 June 1972.

c. Madonna Pfarrer was born 6 November 1947.  She was married 2 December 1967 to Reginald Chamberlain, born 4 March 1947.

aa. Troy Daniel Chamberlain was born 17 June 1968.  Died in car accident 23 May 1988.

bb. Martina Angela Chamberlain was born 17 April 1972.

3. Walter Pfarrer Sr. was born 23 July 1912.  He was married on 1 Feb 1936 to Carherine Garnes, born 19 Dec 1907, died 24 Oct 1945.  He was married a second time on 21 April 1951 to Margaret Wagner, born 18 Feb 1913.

a. Walter Pfarrer Jr. was born 7 August 1937 and died 11 Feb 1982. He was married on 2 Nov 1962 to Gloria Dietz, born 28 Nov 1937.

aa. Lance Allan Pfarrer was born 18 March 1975.

b. Thomas James Pfarrer Sr. was born 13 April 1943.  He was married on 27 April 1968 to Nancy Kline, born 17 Oct 1947. Divorced.

aa. Thomas James Pfarrer Jr was born 11 Oct 1968.

bb. Stephen Brian Pfarrer was born 23 Sept 1970.

c. Dennis James Pfarrer was born 3 July 1952.  (Margaret Wagner).

d. Valerie Pfarrer was born 9 Jan 1954.  She was married 15 Sept 1984 to Bruce Boczkiewicz, born 14 May 1958.

aa. Aaron James Boczkiewicz was born 14 Sept 1989.

bb. Alyssa Leah Boczkiewicz was born 9 Oct 1992.

4. Viola Pfarrer was born 24 Oct 1913.  She died in a car accident 9 July 1990. She was married 19 July 1935 to Lawrence Carolan, born 19 Dec 1912.  

a. Donald Carolan was born 19 Feb 1936.  He was married on 23 May 1959 to Elizabeth Allemand, born 5 August 1939.

aa. Mary Carolan was born 24 Jan 1960.

bb. Michael Carolan was born 4 April 1963.

5. Harvey Pfarrer was born 24 Jan 1918.  He died 28 Feb 1987.  He was married 3 Feb 194x to Mary Tuczkowski, born 11 Feb 1919.  She died 11 June 1989.

6. Ruby Pfarrer was born 10 Feb 1926.  She died 23 June 1992.

D. Ida Ketelhut was born 19 July 1891 in Lebanon.  She died 4 Jan 1944.  She was married on 22 Jan 1914 to Edward Pusch, born 6 Mar 1884, died 1 August 1969.

1. Eleonore Pusch was born 26 Sept 1914.  She died 20 March 1983.  She was  married on 26 Nov 1938 to Arnold Hundt, born 29 May 1905, died 22 Sept 1982.

a. Louis Hundt was born 29 Nov 1940.   She was married on 15 Sept 1952 to Rowland Faber, born 14 Oct 1929.  

aa. Steven Faber was born 8 Nov 1968.

bb. Karen Faber was born 27 August 1970.

2. Leona Pusch was born 10 Feb 1916.  She was married on 22 May 1944 to Ervin Hundt, born 23 Mar 1916.

a. Dennis Hundt was born 15 Dec 1951.  He was married on 7 May 1983 to Sharon Ann Bonlender.

b. Joy Hundt was born 13 July 1953.  She was married on 27 August 1983 to Keith Mueller.

3. Willard Pusch was born 5 March 1918.  He died 7 Dec 1970.  

4. Waldemar Pusch was born 22 July 1919.  He was married 16 June 1943 to Adeline Frey, born 28 May 1918.

a. Dean Busch was born 20 Dec 1950.  He was married on 20 August 1977 to Monica Long, born 27 May 1952. 

b. Kent Pusch was born 17 Dec 1954.

c. Carol Pusch was born 23 Dec 1957.

5. Ruth Pusch was born 27 Feb 1921.  She was married on 14 Nov 1942 to Raymond Schultz, born 12 Nov 1919.

a. Harvey Schultz was born 8 Feb 1944.  He was married on 25 April 1970  to Patricia Ann Schuler, born 10 Jan.

aa. Kristine Schultz was born 3 July 1973.  

bb. Mark Schultz was born 10 Sept 1974.

b. Allen Schultz was born 22 June 1945.  He was married on 20 May  1967 to Nancy Hoefert, born 7 Feb 1947.

aa. Scott Schultz was born 31 Dec 1968.

bb. Brian Schultz was born 13 June 1971.

cc. Brenda Schultz was born 13 June 1971.

c. Robert Schultz was born 11 May 1948.  He was married on 12 June 1971 to Jeanette Jabs, born 7 Feb 1947.  

aa. Michael Robert Schultz was born 11 Oct 1972.

bb. Laura Jean Schultz was born 9 July 1974.

cc. Paul Edward Schultz was born 14 Jan 1982.

d. Mary Ann Schultz was born 19 April 1953.  She was married on 1 Oct 1977 to George Bohn Sr, born 6 Nov 1947.

aa. Angela Bohn was born 25 Feb 1979.

bb. George Raymond Bohn Jr was born 4 Nov 1981.

6. Adeline Pusch was born 13 Nov 1922.  She died 17 April 1991.  She was married on 22 Sept 1951 to Norbert Berndt, born 23 Jan 1926.

a. Jeannie L. Berndt was born 6 May 1953.  She was married on 2 June 1973 to Gerald Lieven, born 2 June 1949.  Divorced.

b. Gerald Edward Berndt was born 18 July 1956.  He was married on 27 Sept 1980 to Gail Louise Budahn.

aa. Jennifer Lynn Berndt was born 7 April 1983.

c. Keith Norbert Berndt was born 13 July 1959.  He was married on 5 Nov 1983 to Doreen May Beine.

aa. Heath Berndt was born 21 March 1986.

bb. Levi Berndt was born 23 Oct 1990.

7. Edward Pusch was born 3 March 1924.

8. Melvin Pusch was born 27 Sept 1927.  He died 14 Feb 1990.  He was married on 26 Jan 1952 to Mary Duehning, born 14 July 1927.

a. Michael Pusch was born 25 Nov 1953.

b. Malinda Pusch was born 9 Oct 1959.

c. Mark Pusch was born 5 August 1962.  He was married on 20 Oct 1990 to Anita Nancy Gartmann.

9. Violet Pusch was born 2 Oct 1928.  She died 13 June 1991.  She was married on 26 Jan 1952 to Delbert Ehlers, born 14 July 1927.

a. Bonnie Jean Ehlers was born 3 May 1953.  She was married on 27 May 1972 to Harold Drake, born 6 August.  They divorced.  She remarried 14 Nov 1992 to Wayne Schultz.

aa. Tammy Sue Drake was born 2 Dec 1975.

bb. Kenneth James Drake was born 31 May 1977.

b. James Wilbert Ehlers was born 16 August 1954.

c. David Thomas Ehlers was born 16 Oct 1964.  He married on 30 Sept 1989 to Susan Weston, born 1 May 1962.

aa. Sara Ehlers was born 9 March 1980.

bb. Loura Ehlers was born 4 Oct 1984.

10. Ruben Pusch was born 20 Dec 1931.  He was married on 15 Oct 1966 to Carol Frank.

a. Gregory Pusch.

11. LaVerne Pusch  was born 8 March 1934.  She was married on 21 Jan 1967 to Richard Zahnow.  

a. Amy Zahnow was born 11 May 1971.

b. Lori Zahnow. 

E. Paul Ketelhut was born 27 Jan 1894 in Lebanon.  He died 4 Feb 1968.  He was married in 1947 to Clara Mertz, born 19 June 1895.  

F. Ella Ketelhut was born 31 Oct 1896 in Lebanon.  She died on 1 Jan 1986.  She was married in September 1919 to Herbert Arndt, born 16 March 1901, died 19 Mar 1974.

1. Sylvester Arndt was born and died 5 Oct 1920.

G. Infant Son Ketelhut was born and died 12 March 1898.

H. Alma Wilhemine Ketelhut was born on 11 Sept 1899.  She died 1 Nov 1968 in Pueblo, Colorado.  She married on 8 July 1917 to Anton Hoefler, born 15 May 1892, died 1 May 1921.  She is buried with him.  After his demise, she married, on 18 March 1922, Jacob Feutz, born 23 March 1887, died 19 Mar 1955.

1. Irene Hoefler was born 15 Nov 1918.  She died in 1921.

2. Genevieve Hoefler was born 25 Nov 1919.  She was married on 7 May 1942  to Jackson Karl Grapes, born 7 May 1918.

a. William Karl Grapes was born 20 Oct 1942.  He was married on 10 May 1969 to Cartherine Inez Ellington, born 9 June 1949.

aa. Kathlyn Marie Grapes was born in 1971.  She was married on 11 April 1992 to David Marsch.

bb. Robby Grapes was born 29 Sept 1976.

b. Russell Roger Grapes Sr. was born 3 Nov 1943.  He was married on 8 October 1963 to Sharon Lee Sullivan, born 14 April 1947.

aa. Russel Roger Grapes Jr. was born 4 August 1964.  He was married on 28 April 1984 to Judith Phipps.

bb. Penny Rose Grapes was born 26 Nov 1973.

c. Karla Lynn Grapes was born 19 Oct 1954.  She was married 3 Oct 1976 to William Joseph Struck, born 14 Aug 1946.  They divorced in 1982.

3.  Tony Hoefler was born and died in 1921.

4. Alma Hoefler was born and died 1921.

5. Ruben Feutz was born 3 August 1923.  He was married on 25 Oct 1943 to Bernice Koeppler, born 31 Jan 1924.

a. Paula Jean Feutz was born 23 Jan 1946.  She died 9 Aug 1991.  She was married on 29 June 1969 to Roger Kuckhan, born Feb 1947.

aa. Brent William Kuckhan was born 16 April 1970.

b. Billy Rae Feutz  was born 11 Nov 1947.  He was married on 31 Aug 1968 to Pamela Hackbart, born 2 Feb 1949.

aa. Jeffrey Jon Feutz was born 22 April 1974.

bb. Jeffrey Patrick Feutz was born 17 Mar 1977.

I.  Lillian Ketelhut was born 26 Feb 1907.  She died 7 Jan 1991.  She was married on 25 Nov 1926 to Barney Zubke, born 27 March 1903, died 4 April 1971.  (She was Rosalie's first child.)

1. Jay Robert Zubke was born 14 Sept 1927.  He was married on 23 July 1955 to June Janet Larson, born 16 June 1927, died 9 Oct 1980.

a. David Jon Zubke was born 3 Jan 1957.  Hee was married on 27 Dec 1980 to Sarah Morton.

aa. Christopher Zubke was born 27 Dec 1989.

b.  Robert Darrall Zubke was born 28 Oct 1958.  

c. Ann Marie Zubke was born 9 April 1968.

2. JoAnn Elaine Zubke was born 14 Jan 1930.  She died on 29 July 1970.  She was married on 10 Nov 1956 to LeRoy St. John born in 1924.

a. Mark St. John was born and died 2 Jan 1959.

b. Craig LeRoy St. John was born 18 Sept 1965.

3. Kenneth H. Zubke was born 16 April 1932.  He died on 13 Dec 1986.  He was married first to LaVerne Lehn, born 23 June 1926.  Then he remarried to Dorothy Campell, born 20 Jan 1940.  

a. Kenneth Zubke Jr. was born 1 Sept 1978.

4. Kay Alice Zubke was born 12 July 1937.  She was married on 8 March 1958 to Atty. Harry B. Oakes, born 25 August 1925. 

a. Pamela Kay Oakes was born 19 June 1959.

b. Harry Boyce Oakes was born 12 May 1961.  He died in car accident 22 Feb 1988.

J. Frances Ketelhut was born 15 October 1908.  She died 17 Feb 1988.  She was married on 25 Nov 1926 to Rodney Templar, born 22 April, died 26 Mar 1988.

1. Harold Rodney Templar was born 12 Jan 1927.  He died.

2. Roger Ray Templar was born 29 April 1928.  He was married on 25 Dec 1955 to Dorothy Kohn, born 27 Dec 1931.

a. Nancy Lynn Templar was born 30 Sept 1956.

b. Jean Marie Templar was born 3 April 1959.  She was married on 10 Oct 1981 to Thomas M. Hartman, born 9 Sept 1959.

aa. Matthew R. Hartman was born 30 July 1983.

bb. Brett T. Hartmann was born 17 August 1987.

3. Dennis Lee Templar was born 3 Jan 1936.  He was married on 2 July 1960 to Susan Voeglie, born 17 Sept 1938.

a. Patricia Ann Templar was born 17 August 1987.

K. Hilda Ketelhut was born 21 Dec 1910.  She died 5 Feb 1985.  She was married on 26 May 1934 to Reinhold Finke, born 13 August 1910, died 18 Sept 1984.

1. Robert Harold Finke was born 10 Oct 1935, died 1 Jan 1992.  He was married on 23 Nov 1957 to Marilyn Laabs, born 23 Sept 1939.

a. Sheryl Finke was born 22 April 1958.  She was married on 27 Feb 1981 to Howard Wondra, born 26 Nov 1956.

b. Robert Finke Jr. was born 30 March 1959.

c. Dori Lynn Finke was born 8 August 1960.  She was married on 3 Oct 1981 to Howard Wondra, born 26 Nov 1956.  

aa. Cloint Robert Wondra was born 7 Nov 1983.

bb. Stacie Wondra was born 8 July 1985.

cc. Bradly James Wondra was born 30 April 1988.

2. Betty Ann Finke was born 20 April  1937.  She was married on 26 Oct 1957 to Vilas Miller, born 8 Oct 1927.

a. Ricky Lee Miller was born 1 Dec 1962.

3. Richard Finke was born and died 27 April 1939.

4. Leon Paul Finke was born 23 August 1940.  He was married on 11 June 1965 to margaret Rediske, born 7 March 1942.

a. Jeffrey Scott Finke was born 21 March 1968.

5. Emily Gladys Finke was born 3 Feb 1942.  She was married on 21 Sept 1953 to Roy Rassmann, born 11 Oct 1939. 

a. Brian Roy Rassmann was born 2 Jan 1964.  He was married on 2 Sept 1989 to Darlene Belling.

aa. Trevoar Brian Rassmann was born 7 Nov 1989.

bb. Tyler Rassman was born 3 Sept 1993.

6. Roland Reinhold Finke was born 2 August 1944.  He was married on12 June 1965 to Joy Ellen Tesch, born 30 June 1944.

a. Richard Lee Finke was born 5 Sept 1967.

b. Bruce Finke was born 18 Jan 1972.

7. Don Wallace Finke was born 6 July 1946.  He was married on 13 Nov 1971 to Donna Rae Backhaus, born 19 Oct 1951.

a. Scott Donald Finke was born 14 May 1977.

b. Kristy Marie Finke was born 31 May 1978.

8. Lois Elsbeth Finke was born 26 Oct 1948.  She died 24 Feb 1949.

9. Judith Kay Finke was born 25 Sept 1950.  She was married 9 Oct 1971 to Ronald Bastian, born 14 July 1949.

a. Bradley Ronald Bastian was born 5 March 1973.

10.  Bonita June Finke was born 11 Feb 1953.  She was married on 2 Nov 1974 to Walter Zastrow, born 5 May 1952.

a. Jennifer Lynn Zastrow was born 4 June 1980.

b. Janell Joan Zastrow was born 4 June 1980.

11. Loris Joy Finke was born 6 Sept 1955.  She was married on 6 Sept 1980 to Jerry Schaefer.

L. Erna Ketelhut was born 9 March 1912.  She died 21 July 1990.  She was married on 1 May 1937 to Walter Rusniak, born 13 April 1915, died 11 Oct 1984.

1. Wallace J. Rusniak was born 19 March 1938.  He was married on 15 Feb 1958 to Rosalia C. Kreuser, born 22 August 1938.

a. Mark James Rusniak was born 28 Nov 1958.

b. Karen Ann Rusniak was born 7 June 1960.

c. James Mike Rusniak was born 24 Dec 1961.

d. Diane Carol Rusniak was born 27 May 1963.

2. Wayne Rusniak was born 2 August 1945.  He was married on 21 August 1965 to Patsy Jean Semler, born 3 Jan 1945.

a. Todd Rusniak was born 25 June 1966.  

b. Troy Rusniak was born 4 Jan 1970.

c. Tammy Rusniak was born 28 March 1973.

M. Leonard Ketelhut was born 17 March 1914.  He died 15 May 1994.  He was married on 8 July 1944 to Ruth pieper, born 16 April 1923.  

1. Marvin H. Ketelhut was born 2 March 1945.  He was married on 12 June 1965 to June Oldenburg, born 14 June 1946.  

a. Ricky Robert Ketelhut was born 28 May 1967.  He was married on 15 July 1992 to Patricia Lang.

aa. Brandon Ketelhut was born 28 June 1991.

bb. Jordan Ketelhut was born 26 Dec 1993.

b. Kristine Machelle Ketelhut was born 15 April 1969.  She was married on 13 Nov 1993 to Darrell Woltman, born 10 April 1966.

2. Larry Leonard Ketelhut was born 21 April 1955.

N. Martin Ketelhut was born 9 Dec 1915,  He died 7 March 1933.

O. Harry Ketelhut was born 6 Dec 1917.  He died 4 March 1989.  He was married on 10 June 1945 to Alice Christian, born 2 April 1926.

1. Gerald Ketelhut was born 31 May 1946.  He was married on 14 Feb 1946 to Kathleen McJunkin.

a. Angela Ketelhut was born 15 July 1976.

b. John Gerald Ketelhut was born 8 Sept 1981.  

2. Geraldine Ketelhut was born 31 May 1946.  She was married on 29 July 1967 to Ronald Wilke Sr, born 17 March 1945.

a. Ronald Wilke Jr ws born 22 Nov 1967.

b. Randy Allen Wilke was born 5 April 1969.

3. Gloria Jean Ketelhut was born 27 August 1955.  She was married on 4 May 1974 to Dennis Baumann.

a. Chad Michael Ketelhut was born 17 July 1978.

b. Josh Ketelhut was born 7 Feb 1984.  

P. Arline Ketelhut was born 12 November 1922.  She was married on 29 May 1943 to Kenneth Luttrop, born 20 May 1919.

1. Jerome William Luttrop was born 23 Nov 1944.  He was married on 22 Aug 1970 to Phyllis Smith, born 26 July 1949.

a. William Luttrop was born 12 Jan 1972, died 14 Jan 1972.

b. Jeff Luttropp was born 21 Oct 1973.

c. Jason Luttrop was born 20 Jan 1975.

2. Kristine Rose Luttropp was born 25 June 1946.  She was married on 8 June 1968 to Curtis Hancock.  

a. Kenneth Floyd Hancock was born 30 Sept 1971.

b. Paul Hancock was born 12 June 1976.

3. Kathleen Ann Luttropp was born 18 April 1948.

4. JoAnn Luttropp was born 9 Dec 1949.  She was married on 8 June 1969 to James R. Heimler, born 31 August 1947.

a. Melissa Joan Heimler was born 6 Dec 1969.

b. James Heimler was born 6 August 1972.

5. Gail Lee Luttropp was born 9 Oct 1951.

6. Sally Jean Luttrop was born 8 June 1953.

7. Joel Kenneth Luttropp was born 14 March 1960.

8. Brian David Luttropp was born 28 April 1964.  Consider Bryan--his Great Grandfather was Daniel Ketelhut!  Some other members of his generation were born in the 1800's!
\vskip 4mm
 The end of the Daniel Ketelhut family 

\pagebreak

{\Huge \noindent The Sharping Family}
\vskip 5mm


The Sharping family records are much less extensive than Ketelhuts!  August Sharping was born in Germany in April 1824.  

He was married to Wilhemina Bremer in Germany.  Wilhemina is a Dutch name.  From records in Dutch St. Maartin there was a lady born by that name born there who was August's age.  The records list marriage and death dates and other significant things about those in them.  No marriage or death dates are listed for her.  Many of the female descendents of August and Wilhemina have steatopygia, an almost strictly African trait. Many of them have very dark skin, highly untypical of northern Europeans.  Some of them have extreme salt sensitivity high blood pressure, a trait found mostly in ``Transported Africans''.  Some family members have clearly African features.  

She spent at least  her later life in Germany.  Their children migrated to America, and after she died, August joined them.  He died on 24 May 1896.  He is buried in the Kimball, S.Dak. cemetary.  The the tomb stone is made of marble, and also has the names of several of his grandchildren who died also around 1896 from a severe diptheria epidemic.  Many decendents still live from Kimball, SD, to Chamberlain.

I. Amelia Sharping was born about 1860.  She died about 1939.  She married  Charlie Goetsch.  They are buried in the Chamberlain S.D. cemetary.  

A. Arthur Goetsch married Ester Swanson.

B. Charlie Goetsch

C. Ida Goetsch married a Mr. Isburg.

D. Lucy Goetsch married a Mr. Ostert

E. Oscar Goetsch married  Mabel Holstein

F. Pearl Goetsch married Walter Busack.

G. Richard Goetsch was born in 1896.  He died in May of 1995.  He was married to Meta Fascher.  They celebrated their 70th wedding anniversary in 1989. 

II. Augusta Sharping was born on 25 September 1862 in Labetzov, Germany.  She died in 1943.  She married Johann Ketelut, their family is listed under the Ketelhut section.

III. A. Otto  Sharping was married to Charlotte Haferbecker.

A. Anna Emilie Sharping was married to Joseph Nedved.

B. Eda Ellen Sharping was married to Harold Gilchrist.  

C. Frank Sharping was married to Grace Harris.

1. Frank Sharping II was born in 1923 and died in July of 1991.

2. Robert Lee Sharping was born in 1925.

3. Raymond Sharping was born in 1927.

4. Lyden Sharping was born in 1931.

D. John Henry Sharping was married to Josephine Radak.

IV. Albert Sharping

V. Bertha Sharping was married to a Mr. Peters.

VI. Hermann Sharping

VII. Mary Emilie Sharping was married to Amos Gaulke

VIII. Mathilda Ann Sharping was married to Peter Simon

IX. Nella Edith Sharping was married to William Rohrs.

X. Otto Sharping

XI.  Wilhemina Anna Sharping was married to Charles Bause.

\vskip 4mm
End of Sharping family
\pagebreak

{\Huge \noindent Kenneth Merril's Advice to Writers}
\vskip 5mm


1. Watch your speling.  Writrs who mispele a lott of words are propperly reguarded as illiterate.

2. Dont forget the apostrophe where its needed.  But dont stick where theres no need for it. A writers reputation hangs on such apparent trifle's.  

3. Be careful of the grammatical case of pronouns.  Mistakes here can give a bad name to we writers (i.e. to you and I.)

4. Don't exaggerate.  Overstate always causes infinite harm.

5. Avoiding foreign phrases as a conditio sine qua non for the writer who wants to be klar und deutlich, especially if he is writing for oi polloi.  Le mot juste is most likely to be found in one's own lengua madre.  

6. The careful writer must take panes with homophones which are all easy to confuse.  Though understandable, such confusions great on the reader's nerves.

7. Beware of the dangling participle.  Forgetting this admonition, infelicitous phrases creap into our writing.

8.  Cliches should be avoided like the plague.  However, hackeyed languages is not likely to be a problem for the writer who, since he was knee high to a grasshopper, has built a better mouse trap and has kept his shoulder to the wheel.

9.  Keep your language simple.  Eschew sesquipedalian locutions and fustian rhetoric.  Stay clear of the crepuscular--nay tenebrific and fuliginous--regions of orotund sonorities.

10.  Avoid vogue words.  Hopefully, the writer will remember that his words impact the reader at the dynamic inteface of creative thought and action.  To be viable, the writer's parameters must enable him to engage the knowledgeable reader in a meaningful dialogue--especially at this point in time when people tend to prioritise their priorities optimally.

11. Avoid profane or abusive language.  It is a damned outrage how many knuckle-dragging slobs vilify people with whom they disagree.

12.  When the passive voice is used, a certain flaccidity and awkwardness is introduced into the writing style.  I have been struck by the thought that a law should be passed whereby the passive voice would not be permitted to be used unless an official is applied to and a special dispensation is granted.

13.  Beware of the Gemini trap.  Many pairs of English words differ only in their suffixes.  It is incredulous how neglibible writers are about this problem.  The writer who would cultivate a perspicacious style cannot afford to flaunt the good council  offered in this rule--though some people actually flout their infelicities as a badge of distinction.  Such behaviour is contempuous.

\end{document}
